### 2025-02-02 src/article.tex
init paper

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\onehalfspacing

% Define keywords command
\providecommand{\keywords}[1]{\textbf{Keywords:} #1}

\title{\rule{\textwidth}{1pt}\\[0.5cm]
Payout profile approximation with vanilla European options\\[0.5cm]
\rule{\textwidth}{1pt}}
\author{\small Vlad Kochetov \\ \small Faculty of Mechanics and Mathematics, \\ \small Taras Shevchenko National University of Kyiv \\ \small \texttt{vladkoch@knu.ua}}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper explores the methodology for approximating complex payout profiles using a combination of vanilla European options. We present a mathematical framework that allows for the decomposition of arbitrary payout structures into a series of call and put options with varying strike prices. The approach is validated through numerical examples and practical applications in financial engineering. The results demonstrate the effectiveness of this method in replicating complex payouts with high accuracy while maintaining computational efficiency.
\end{abstract}

\keywords{Vanilla options, payout profile, financial engineering, option pricing, approximation}

\section{Introduction}
The ability to replicate complex financial instruments using simpler, more liquid derivatives is a cornerstone of modern financial engineering. Vanilla European options, due to their simplicity and widespread availability, serve as ideal building blocks for such approximations. This paper introduces a novel approach to approximating arbitrary payout profiles using a combination of these options.

\section{Literature Review}
The concept of replicating complex payouts using simpler instruments has been extensively studied in the literature. \cite{hull2018options} provides a comprehensive overview of option pricing and replication strategies. Recent work by \cite{smith2020financial} has explored the use of machine learning techniques for payout approximation, though their focus was primarily on exotic options.

\section{Methodology}
\subsection{Mathematical Framework}
Let \( V(S, T) \) represent the value of a target payout profile at maturity \( T \) as a function of the underlying asset price \( S \). We aim to approximate \( V(S, T) \) using a combination of European call and put options:

\begin{equation}
V(S, T) \approx \sum_{i=1}^{n} \alpha_i C(S, K_i, T) + \beta_i P(S, K_i, T)
\end{equation}

where \( C(S, K_i, T) \) and \( P(S, K_i, T) \) are the prices of call and put options with strike \( K_i \), and \( \alpha_i, \beta_i \) are the corresponding weights.

\subsection{Numerical Implementation}
The approximation is achieved through the following steps:
\begin{enumerate}
    \item Discretization of the payout profile
    \item Optimization of option weights
    \item Error minimization using least squares
\end{enumerate}

\section{Results}
The proposed methodology was tested on several complex payout profiles, including digital options and barrier options. The results demonstrate that the approximation error decreases significantly as the number of vanilla options increases, with a mean absolute error of less than 1\% for most cases.

\section{Conclusion}
This paper presents a robust method for approximating complex payout profiles using vanilla European options. The approach offers significant advantages in terms of computational efficiency and practical implementation, making it a valuable tool for financial engineers and practitioners.

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2025-02-02 src/article.tex
formatting

@@
 
-\title{\rule{\textwidth}{1pt}\\[0.5cm]
-Payout profile approximation with vanilla European options\\[0.5cm]
+\title{\rule{\textwidth}{2pt}\\[0.5cm]
+\textbf{Payout profile approximation with vanilla European options}\\[0.5cm]
 \rule{\textwidth}{1pt}}
-\author{\small Vlad Kochetov \\ \small Faculty of Mechanics and Mathematics, \\ \small Taras Shevchenko National University of Kyiv \\ \small \texttt{vladkoch@knu.ua}}
+\author{\small \textbf{Vlad Kochetov} \\
+    \small Faculty of Mechanics and Mathematics, \\
+    \small Taras Shevchenko National University of Kyiv \\
+    \small \texttt{vladkoch@knu.ua}
+}
 \date{\today}
@@
 
-\keywords{Vanilla options, payout profile, financial engineering, option pricing, approximation}
+\keywords{Vanilla Options, 
+          Payout Profile, 
+          Financial Engineering, 
+          Option Pricing, 
+          Approximation,
+          Numerical Methods}
 

### 2025-02-02 latex/article.tex
renaming
keywords

--- 2025-02-02 src/article.tex
@@
 
-\title{\rule{\textwidth}{2pt}\\[0.5cm]
+\title{\rule{\textwidth}{4pt}\\[0.5cm]
 \textbf{Payout profile approximation with vanilla European options}\\[0.5cm]
-\rule{\textwidth}{1pt}}
+\rule{\textwidth}{2pt}}
 \author{\small \textbf{Vlad Kochetov} \\
@@
 This paper explores the methodology for approximating complex payout profiles using a combination of vanilla European options.
-We present a mathematical framework that allows for the decomposition of arbitrary payout structures into a series of call and put options with varying strike prices.
+The mathematical framework is presented that allows for the decomposition of arbitrary payout structures into a series of call and put options with varying strike prices.
 The approach is validated through numerical examples and practical applications in financial engineering.
@@
 
-\keywords{Vanilla Options, 
+\keywords{
+    \small{
+        Vanilla Options, 
         Payout Profile, 
@@
         Approximation, 
-          Numerical Methods}
+        Numerical Methods,
+        Quantitative Finance,
+        Financial Derivatives,
+        Computational Finance
+    }
+}
 
@@
 Vanilla European options, due to their simplicity and widespread availability, serve as ideal building blocks for such approximations.
-This paper introduces a novel approach to approximating arbitrary payout profiles using a combination of these options.
+This paper introduces an approach to approximating arbitrary payout profiles using a combination of these options.
 

### 2025-02-09 latex/article.tex
numerical implementation

@@
 \onehalfspacing
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 \title{\rule{\textwidth}{4pt}\\[0.5cm]
-\textbf{Payout profile approximation with vanilla European options}\\[0.5cm]
+\textbf{Discrete payout profile approximation with vanilla European options}\\[0.5cm]
 \rule{\textwidth}{2pt}}
@@
 \begin{abstract}
-This paper explores the methodology for approximating complex payout profiles using a combination of vanilla European options.
-The mathematical framework is presented that allows for the decomposition of arbitrary payout structures into a series of call and put options with varying strike prices.
-The approach is validated through numerical examples and practical applications in financial engineering.
-The results demonstrate the effectiveness of this method in replicating complex payouts with high accuracy while maintaining computational efficiency.
+This paper explores the methodology for approximating complex payout profiles using a
+combination of vanilla European options. The mathematical framework is presented that
+allows for the decomposition of arbitrary payout structures into a series of call and
+put options with varying strike prices. The approach is validated through numerical
+examples and practical applications in financial engineering. The results demonstrate
+the effectiveness of this method in replicating complex payouts.
 \end{abstract}
+
+\newpage
 
@@
 \section{Introduction}
-The ability to replicate complex financial instruments using simpler, more liquid derivatives is a cornerstone of modern financial engineering.
-Vanilla European options, due to their simplicity and widespread availability, serve as ideal building blocks for such approximations.
-This paper introduces an approach to approximating arbitrary payout profiles using a combination of these options.
+The ability to replicate complex financial instruments using simpler, more liquid
+derivatives is a cornerstone of modern financial engineering. Vanilla European options,
+due to their simplicity and widespread availability, serve as ideal building blocks
+for such approximations. This paper introduces an approach to approximating arbitrary
+payout profiles using a combination of these options.
 
 \section{Literature Review}
-The concept of replicating complex payouts using simpler instruments has been extensively studied in the literature.
-\cite{hull2018options} provides a comprehensive overview of option pricing and replication strategies.
-Recent work by \cite{smith2020financial} has explored the use of machine learning techniques for payout approximation, though their focus was primarily on exotic options.
+Foundational work by Black and Scholes \cite{black1973pricing} established the theoretical framework for option pricing under geometric Brownian motion assumptions.
+Subsequent research has extended these principles to various derivative pricing applications.
 
 \section{Methodology}
+\subsection{Model Assumptions}
+The analysis assumes the underlying asset follows geometric Brownian motion with constant drift $\mu$ and volatility $\sigma$ \cite{black1973pricing}:
+\begin{equation}
+dS_t = \mu S_t dt + \sigma S_t dW_t
+\end{equation}
+where $W_t$ is a Wiener process. Option pricing utilizes the Black-Scholes framework \cite{black1973pricing} for fair value calculation, incorporating risk-neutral valuation principles.
+
 \subsection{Mathematical Framework}
-Let \( V(S, T) \) represent the value of a target payout profile at maturity \( T \) as a function of the underlying asset price \( S \).
-We aim to approximate \( V(S, T) \) using a combination of European call and put options:
+Let \( V(S, T) \) represent the value of a target payout profile at maturity \( T \)
+as a function of the underlying asset price \( S \). We construct an approximation
+using \( n \) call options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
 
 \begin{equation}
-V(S, T) \approx \sum_{i=1}^{n} \alpha_i C(S, K_i, T) + \beta_i P(S, K_i, T)
+V(S, T) \approx \lambda S + \sum_{i=1}^{n} \alpha_i C(S, K_i, T) + \sum_{j=1}^{m} \beta_j P(S, K_j, T)
 \end{equation}
 
-where \( C(S, K_i, T) \) and \( P(S, K_i, T) \) are the prices of call and put options with strike \( K_i \), and \( \alpha_i, \beta_i \) are the corresponding weights.
+where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) are
+option weights. The optimal weights are found by solving the regularized least squares
+problem:
+
+\begin{equation}
+\min_{\boldsymbol{\theta}} \int_{S_{\min}}^{S_{\max}} \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + \gamma \|\boldsymbol{\theta}\|_2^2
+\end{equation}
+
+where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
+the position weights, \( \gamma \) is the regularization parameter, and
+\( S_{\min}, S_{\max} \) define the approximation domain.
+
+Discretizing the integral and using matrix notation, we solve:
+
+\begin{equation}
+\boldsymbol{\theta}^* = \argmin_{\boldsymbol{\theta}} \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + \gamma \|\boldsymbol{\theta}\|_2^2
+\end{equation}
+
+where the design matrix \( \mathbf{A} \) contains option payoffs and spot positions
+evaluated at discrete price points \( \{S_k\}_{k=1}^N \), and \( \mathbf{b} \) is
+the vector of target payout values.
 
 \subsection{Numerical Implementation}
-The approximation is achieved through the following steps:
-\begin{enumerate}
-    \item Discretization of the payout profile
-    \item Optimization of option weights
-    \item Error minimization using least squares
-\end{enumerate}
+The discrete optimization problem is solved using regularized least squares:
+\begin{equation}
+\boldsymbol{\theta}^* = (\mathbf{A}^\top \mathbf{A} + \gamma \mathbf{I})^{-1} \mathbf{A}^\top \mathbf{b}
+\end{equation}
+
+where:
+\begin{itemize}
+\item \( \mathbf{A} \in \mathbb{R}^{N \times (n+m+1)} \): Matrix of basis payoffs
+\item \( \mathbf{b} \in \mathbb{R}^N \): Target payoff values
+\item \( \gamma \): Regularization parameter controlling solution smoothness
+\item \( \mathbf{I} \): Identity matrix for L2 regularization
+\end{itemize}
+
+The evaluation points \( \{S_k\} \) are typically distributed around the current
+spot price to emphasize approximation accuracy in relevant price regions.
 
 \section{Results}
-The proposed methodology was tested on several complex payout profiles, including digital options and barrier options.
-The results demonstrate that the approximation error decreases significantly as the number of vanilla options increases, with a mean absolute error of less than 1\% for most cases.
+\begin{figure}[htbp]
+\centering
+\input{regularization_comparison.tex}
+\caption{Comparison of L1 and L2 regularization methods for payout profile approximation}
+\label{fig:regularization}
+\end{figure}
 
 \section{Conclusion}
-This paper presents a robust method for approximating complex payout profiles using vanilla European options.
-The approach offers significant advantages in terms of computational efficiency and practical implementation, making it a valuable tool for financial engineers and practitioners.
 

### 2025-02-09 code/approximation.py

@@ -1,0 +1,140 @@
+import numpy as np
+from scipy.optimize import minimize
+from typing import Callable, Tuple
+import matplotlib.pyplot as plt
+from sklearn.linear_model import Lasso
+import tikzplotlib  # Добавить в импорты
+
+def create_basis_functions(strikes: list[float], spot: float) -> list[Callable[[float], float]]:
+    """Generate call/put payoff functions for given strikes"""
+    basis = []
+    for K in strikes:
+        # Call option payoff: max(S - K, 0)
+        basis.append(lambda S, K=K: np.maximum(S - K, 0))
+        # Put option payoff: max(K - S, 0) 
+        basis.append(lambda S, K=K: np.maximum(K - S, 0))
+    return basis
+
+def approximate_payout(
+    target_payout: Callable[[float], float],
+    strikes: list[float],
+    spot: float,
+    regularization: float = 0.05,
+    method: str = 'l2'
+) -> Tuple[np.ndarray, float]:
+    """
+    Approximate target payout using vanilla options
+    
+    Args:
+        target_payout: Function of S (spot price) to approximate
+        strikes: Available strike prices
+        spot: Current spot price
+        regularization: L2 regularization parameter
+        method: Method of regularization ('l2' or 'l1')
+        
+    Returns:
+        Tuple (weights, lambda) where:
+        - weights: Coefficients for options
+        - lambda: Spot position coefficient
+    """
+    # Generate evaluation points around spot price
+    S_values = np.linspace(0.5*spot, 1.5*spot, 100)
+    
+    # Create basis functions (calls/puts)
+    basis = create_basis_functions(strikes, spot)
+    
+    # Add spot position (lambda*S) to the basis
+    basis.append(lambda S: S)  # Lambda term
+    
+    # Build design matrix
+    A = np.array([[f(S) for f in basis] for S in S_values])
+    b = np.array([target_payout(S) for S in S_values])
+    
+    if method == 'l2':
+        # Solve regularized least squares
+        solution = np.linalg.lstsq(
+            A.T @ A + regularization * np.eye(A.shape[1]),
+            A.T @ b,
+            rcond=None
+        )[0]
+    elif method == 'l1':
+        # L1 регуляризация с использованием Lasso
+        model = Lasso(alpha=regularization, fit_intercept=False, max_iter=10000)
+        model.fit(A, b)
+        solution = model.coef_
[…]

### 2025-02-09 code/pricing.py

@@ -1,0 +1,75 @@
+from math import log, sqrt, exp
+from scipy.stats import norm
+
+def black_scholes_price(
+    S: float,         # Current asset price
+    K: float,         # Strike price
+    T: float,         # Time to maturity (in years)
+    r: float,         # Risk-free interest rate
+    sigma: float,     # Asset volatility
+    option_type: str  # Option type: 'call' or 'put'
+) -> float:
+    """
+    Calculates the price of a European option using the Black-Scholes model.
+
+    Parameters:
+    S: Current asset price
+    K: Strike price
+    T: Time to maturity
+    r: Risk-free interest rate
+    sigma: Asset volatility
+    option_type: Option type ('call' or 'put')
+
+    Returns:
+    Option price
+    """
+    d1 = (log(S / K) + (r + 0.5 * sigma**2) * T) / (sigma * sqrt(T))
+    d2 = d1 - sigma * sqrt(T)
+    
+    if option_type == 'call':
+        price = S * norm.cdf(d1) - K * exp(-r * T) * norm.cdf(d2)
+    elif option_type == 'put':
+        price = K * exp(-r * T) * norm.cdf(-d2) - S * norm.cdf(-d1)
+    else:
+        raise ValueError("Unsupported option type. Use 'call' or 'put'.")
+    
+    return price
+
+
+def black_scholes_greeks(
+    S: float, K: float, T: float, r: float, sigma: float, option_type: str
+) -> dict[str, float]:
+    """
+    Calculates the Greeks for a European option using the Black-Scholes model.
+
+    Parameters:
+    S: Current asset price
+    K: Strike price
+    T: Time to maturity
+    r: Risk-free interest rate
+    sigma: Asset volatility
+    option_type: Option type ('call' or 'put')
+
+    Returns:
+    Dictionary with Greeks: delta, gamma, vega, theta, rho
+    """
+    d1 = (log(S / K) + (r + 0.5 * sigma**2) * T) / (sigma * sqrt(T))
+    d2 = d1 - sigma * sqrt(T)
+    
+    delta = norm.cdf(d1) if option_type == 'call' else -norm.cdf(-d1)
+    gamma = norm.pdf(d1) / (S * sigma * sqrt(T))
+    vega = S * norm.pdf(d1) * sqrt(T)
+    theta = (-S * norm.pdf(d1) * sigma / (2 * sqrt(T)) 
[…]

### 2025-02-09 latex/article.tex
edge

@@
 \section{Results}
+\subsection{Distribution-Based Trading Strategy}
+The approximation method enables novel trading strategies that exploit distributional forecasts rather than direct price predictions.
+By constructing portfolios that profit from specific distribution characteristics (e.g., fat tails or volatility clustering), traders can:
+
+\begin{itemize}
+\item Hedge against forecasted distribution features
+\item Express views on higher moments of price distribution
+\item Implement volatility surface arbitrage strategies
+\end{itemize}
+
+The key advantage emerges when combining the approximation with distribution forecasts $\mathbb{P}(S_T)$:
+
+\begin{equation}
+\mathbb{E}[V(S_T)] = \int_{0}^{\infty} V(S) \mathbb{P}(S_T = S) dS
+\end{equation}
+
+Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payout under forecasted distribution:
+
+\begin{equation}
+\boldsymbol{\theta}^* = \argmax_{\boldsymbol{\theta}} \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - \lambda \text{Var}\left(\hat{V}(S_T;\boldsymbol{\theta})\right)
+\end{equation}
+
+where $\lambda$ represents risk aversion parameter.
+
 \begin{figure}[htbp]

### 2025-02-09 latex/article.tex
paper name

@@
 \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
-
-\title{\rule{\textwidth}{4pt}\\[0.5cm]
-\textbf{Discrete payout profile approximation with vanilla European options}\\[0.5cm]
+\title{\rule{\textwidth}{4pt}\\
+\textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm]
+Regularized Payout Approximation in Derivative Space}\\[0.2cm]
 \rule{\textwidth}{2pt}}
@@
 
-where:
-\begin{itemize}
-\item \( \mathbf{A} \in \mathbb{R}^{N \times (n+m+1)} \): Matrix of basis payoffs
-\item \( \mathbf{b} \in \mathbb{R}^N \): Target payoff values
-\item \( \gamma \): Regularization parameter controlling solution smoothness
-\item \( \mathbf{I} \): Identity matrix for L2 regularization
-\end{itemize}
-
-The evaluation points \( \{S_k\} \) are typically distributed around the current
-spot price to emphasize approximation accuracy in relevant price regions.
+where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ controls solution smoothness through regularization, and $\mathbf{I}$ denotes the identity matrix for L2 regularization.
+Evaluation points $\{S_k\}$ are typically distributed around the current spot price to emphasize approximation accuracy in relevant price regions.
 
@@
 The approximation method enables novel trading strategies that exploit distributional forecasts rather than direct price predictions.
-By constructing portfolios that profit from specific distribution characteristics (e.g., fat tails or volatility clustering), traders can:
-
-\begin{itemize}
-\item Hedge against forecasted distribution features
-\item Express views on higher moments of price distribution
-\item Implement volatility surface arbitrage strategies
-\end{itemize}
+Traders can hedge against forecasted distribution features, express views on higher moments of price distribution, and implement volatility surface arbitrage strategies through carefully constructed option portfolios.
 

### 2025-02-12 code/distrofit.py
cite

@@ -1,0 +1,107 @@
+import numpy as np
+from typing import Callable
+import plotly.graph_objects as go
+from plotly.subplots import make_subplots
+
+class DistributionToPayout:
+    """
+    Converts probability distribution forecast to payout function
+    
+    Parameters:
+        bins (np.ndarray): Array of bin edges (N+1 elements)
+        probabilities (np.ndarray): Probability for each bin (N elements)
+        payout_scale (float): Scaling factor for payout amounts
+    """
+    def __init__(
+        self,
+        bins: np.ndarray,
+        probabilities: np.ndarray,
+        payout_scale: float = 100.0
+    ):
+        self.bins = bins
+        self.probabilities = probabilities
+        self.payout_scale = payout_scale
+        
+        # Validate inputs
+        assert len(bins) == len(probabilities) + 1, "Invalid bins-probabilities shape"
+        assert np.isclose(probabilities.sum(), 1.0), "Probabilities must sum to 1"
+        
+    def get_payout_function(self) -> Callable[[float], float]:
+        """Create piecewise constant payout function"""
+        # Calculate midpoints for each bin
+        midpoints = (self.bins[1:] + self.bins[:-1]) / 2
+        
+        # Calculate payout weights: inverse probability weighting
+        weights = self.payout_scale * (1 / (self.probabilities + 1e-8))
+        
+        # Normalize weights to [0, 1] range
+        weights /= weights.max()
+        
+        def payout(S: float) -> float:
+            # Find bin index for given price
+            bin_idx = np.searchsorted(self.bins, S, side='right') - 1
+            if 0 <= bin_idx < len(weights):
+                return weights[bin_idx] * self.probabilities[bin_idx]
+            return 0.0  # Out of range
+            
+        return payout
+
+    def plot_distribution(self):
+        """Visualize probability distribution and payout function in browser"""
+        # Create figure with secondary y-axis
+        fig = make_subplots(rows=2, cols=1, shared_xaxes=True)
+        
+        # Bin centers and widths
+        centers = (self.bins[1:] + self.bins[:-1]) / 2
+        
+        # Plot probability distribution
+        fig.add_trace(
+            go.Bar(x=centers, y=self.probabilities, name="Probability Distribution"),
+            row=1, col=1
+        )
[…]

### 2025-02-12 code/distrofit_2.py

@@ -1,0 +1,98 @@
+import numpy as np
+from typing import Callable
+import matplotlib.pyplot as plt
+
+class DistributionToPayout:
+    """
+    Converts probability distribution forecast to payout function
+    
+    Parameters:
+        bins (np.ndarray): Array of bin edges (N+1 elements)
+        probabilities (np.ndarray): Probability for each bin (N elements)
+        payout_scale (float): Scaling factor for payout amounts
+    """
+    def __init__(
+        self,
+        bins: np.ndarray,
+        probabilities: np.ndarray,
+        payout_scale: float = 100.0
+    ):
+        self.bins = bins
+        self.probabilities = probabilities
+        self.payout_scale = payout_scale
+        
+        # Validate inputs
+        assert len(bins) == len(probabilities) + 1, "Invalid bins-probabilities shape"
+        assert np.isclose(probabilities.sum(), 1.0), "Probabilities must sum to 1"
+        
+    def get_payout_function(self) -> Callable[[float], float]:
+        """Create piecewise constant payout function"""
+        # Calculate midpoints for each bin
+        midpoints = (self.bins[1:] + self.bins[:-1]) / 2
+        
+        # Calculate payout weights: inverse probability weighting
+        weights = self.payout_scale * (1 / (self.probabilities + 1e-8))
+        
+        # Normalize weights to [0, 1] range
+        weights /= weights.max()
+        
+        def payout(S: float) -> float:
+            # Find bin index for given price
+            bin_idx = np.searchsorted(self.bins, S, side='right') - 1
+            if 0 <= bin_idx < len(weights):
+                return weights[bin_idx] * self.probabilities[bin_idx]
+            return 0.0  # Out of range
+            
+        return payout
+
+    def plot_distribution(self, save_path: str = None):
+        """Visualize probability distribution and payout function"""
+        fig, (ax1, ax2) = plt.subplots(2, 1, figsize=(10, 8), sharex=True)
+        
+        # Bin centers and widths
+        centers = (self.bins[1:] + self.bins[:-1]) / 2
+        widths = self.bins[1:] - self.bins[:-1]
+        
+        # Plot probability distribution
+        ax1.bar(centers, self.probabilities, width=widths, alpha=0.7)
[…]

### 2025-02-12 latex/article.tex
cite
tikz

@@
 \usepackage{setspace}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.18}
 \onehalfspacing
 \DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\usepackage{amsmath, amssymb, amsthm}
 
@@
 \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm]
-Regularized Payout Approximation in Derivative Space}\\[0.2cm]
+Regularized Payout Approximation in Discrete Space}\\[0.2cm]
 \rule{\textwidth}{2pt}}
@@
         Financial Derivatives,
-        Computational Finance
+        Computational Finance,
+        Distribution Forecasts,
+        Portfolio Construction,
+        Option Trading
     }
@@
 \section{Literature Review}
-Foundational work by Black and Scholes \cite{black1973pricing} established the theoretical framework for option pricing under geometric Brownian motion assumptions.
-Subsequent research has extended these principles to various derivative pricing applications.
 
@@
 \subsection{Model Assumptions}
-The analysis assumes the underlying asset follows geometric Brownian motion with constant drift $\mu$ and volatility $\sigma$ \cite{black1973pricing}:
-\begin{equation}
-dS_t = \mu S_t dt + \sigma S_t dW_t
-\end{equation}
-where $W_t$ is a Wiener process. Option pricing utilizes the Black-Scholes framework \cite{black1973pricing} for fair value calculation, incorporating risk-neutral valuation principles.
 
 \subsection{Mathematical Framework}
-Let \( V(S, T) \) represent the value of a target payout profile at maturity \( T \)
-as a function of the underlying asset price \( S \). We construct an approximation
-using \( n \) call options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
+Let \( V(S) \) represent the value of a target payout profile as a function of the underlying asset price \( S \).
+We construct an approximation using \( n \) call options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
 
 \begin{equation}
-V(S, T) \approx \lambda S + \sum_{i=1}^{n} \alpha_i C(S, K_i, T) + \sum_{j=1}^{m} \beta_j P(S, K_j, T)
+V(S) \approx \lambda S + \sum_{i=1}^{n} \alpha_i C(S, K_i) + \sum_{j=1}^{m} \beta_j P(S, K_j)
 \end{equation}
@@
 option weights. The optimal weights are found by solving the regularized least squares
-problem:
+problem with either L2 (Ridge) or L1 (Lasso) regularization:
 
 \begin{equation}
-\min_{\boldsymbol{\theta}} \int_{S_{\min}}^{S_{\max}} \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + \gamma \|\boldsymbol{\theta}\|_2^2
+\min_{\boldsymbol{\theta}} \int_{S_{\min}}^{S_{\max}} \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + \gamma \|\boldsymbol{\theta}\|_p^p
 \end{equation}
@@
 where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
-the position weights, \( \gamma \) is the regularization parameter, and
-\( S_{\min}, S_{\max} \) define the approximation domain.
+the position weights, \( \gamma \) is the regularization parameter, 
+\( S_{\min}, S_{\max} \) define the approximation domain, and \( p \) determines
+the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight distributions,
+while the L1 norm (\(p=1\)) tends to produce sparse solutions by setting some weights
+exactly to zero, which can be beneficial when portfolio simplicity or transaction costs
+are important considerations.
 
@@
 \begin{equation}
-\boldsymbol{\theta}^* = \argmin_{\boldsymbol{\theta}} \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + \gamma \|\boldsymbol{\theta}\|_2^2
+\boldsymbol{\theta}^* = \argmin_{\boldsymbol{\theta}} \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + \gamma \|\boldsymbol{\theta}\|_p^p
 \end{equation}
@@
 \subsection{Numerical Implementation}
-The discrete optimization problem is solved using regularized least squares:
+The discrete optimization problem with L2 regularization has a closed-form solution:
 \begin{equation}
@@
 
-where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ controls solution smoothness through regularization, and $\mathbf{I}$ denotes the identity matrix for L2 regularization.
+where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ controls solution smoothness through regularization, and $\mathbf{I}$ denotes the identity matrix.
 Evaluation points $\{S_k\}$ are typically distributed around the current spot price to emphasize approximation accuracy in relevant price regions.
+The L1-regularized problem is solved using iterative optimization methods.
 
 \section{Results}
-\subsection{Distribution-Based Trading Strategy}
+\subsection{Distribution-Based Trading}
 The approximation method enables novel trading strategies that exploit distributional forecasts rather than direct price predictions.
@@
 \input{regularization_comparison.tex}
-\caption{Comparison of L1 and L2 regularization methods for payout profile approximation}
+\caption{Comparison of regularization methods using 9 strike prices.}
 \label{fig:regularization}

### 2025-02-12 latex/regularization_comparison.tex
tikz

\begin{tikzpicture}
\begin{axis}[
    width=0.9\textwidth,
    height=6cm,
    grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
    xlabel style={font=\tiny},
    ylabel style={font=\tiny},
    tick label style={font=\tiny},
    title style={font=\small},
    legend style={font=\tiny, at={(0.02,0.98)}, anchor=north west},
    xlabel={Underlying Asset Price},
    ylabel={Payout},
    title={Regularization Methods Comparison}
]

\addplot[thick, black] table[x index=0,y index=1] {regularization_comparison.dat};
\addlegendentry{Target Payout}

\addplot[thick, dashed, red] table[x index=0,y index=2] {regularization_comparison.dat};
\addlegendentry{L2 Regularization Approximation}

\addplot[thick, dashdotted, blue] table[x index=0,y index=3] {regularization_comparison.dat};
\addlegendentry{L1 Regularization Approximation}

\end{axis}
\end{tikzpicture}

### 2025-02-12 code/approximation.py

@@ -1,9 +1,10 @@
 import numpy as np
 from scipy.optimize import minimize
 from typing import Callable, Tuple
+import matplotlib
+matplotlib.use('Agg')  # Добавить в начало файла
 import matplotlib.pyplot as plt
 from sklearn.linear_model import Lasso
-import tikzplotlib  # Добавить в импорты
 
 def create_basis_functions(strikes: list[float], spot: float) -> list[Callable[[float], float]]:
     """Generate call/put payoff functions for given strikes"""
@@ -99,33 +100,58 @@ def example_usage():
     approx_l2 = sum(w*f(S_test) for w, f in zip(weights_l2, basis)) + lambda_l2*S_test
     approx_l1 = sum(w*f(S_test) for w, f in zip(weights_l1, basis)) + lambda_l1*S_test
     
-    # Create figure
+    # Create figure with improved styling
     plt.figure(figsize=(14, 7))
     plt.plot(S_test, target_values, 'k-', label='Target Payout', lw=3)
-    plt.plot(S_test, approx_l2, '--', label='L2 Regularization', lw=2)
-    plt.plot(S_test, approx_l1, '-.', label='L1 Regularization', lw=2)
-    plt.title("Regularization Methods Comparison", fontsize=14)
-    plt.xlabel("Underlying Asset Price", fontsize=12)
-    plt.ylabel("Payout", fontsize=12)
-    plt.legend(fontsize=12, loc='upper left')
+    plt.plot(S_test, approx_l2, '--', label='L2 Regularization Approximation', lw=2)
+    plt.plot(S_test, approx_l1, '-.', label='L1 Regularization Approximation', lw=2)
+    plt.title("Regularization Methods Comparison", fontsize=9)
+    plt.xlabel("Underlying Asset Price", fontsize=8)
+    plt.ylabel("Payout", fontsize=8)
+    plt.legend(fontsize=8, loc='upper left')
     plt.grid(True, alpha=0.3)
+    plt.tick_params(labelsize=7)
     
-    # Сохраняем в TikZ
-    tikzplotlib.save("regularization_comparison.tex",
-                     axis_width="\\textwidth",
-                     axis_height="8cm",
-                     textsize=10)
+    # Save data for pgfplots
+    with open("../latex/regularization_comparison.dat", "w") as f:
+        f.write("# S target l2 l1\n")
[…]

### 2025-02-12 latex/article.tex
figure

@@
         Distribution Forecasts,
-        Portfolio Construction,
         Option Trading
@@
 
+\begin{figure}[htbp]
+\centering
+\input{regularization_comparison.tex}
+\caption{Comparison of L1 and L2 regularization}
+\label{fig:regularization}
+\end{figure}
+
+Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization approaches in approximating a complex payout profile.
+The target function combines linear, sinusoidal, and power-law segments, presenting a challenging test case.
+Both methods achieve good approximation quality, with L2 regularization providing slightly smoother results and L1 regularization favoring a sparser representation with fewer non-zero option weights.
+
 \section{Results}
@@
 
-\begin{figure}[htbp]
-\centering
-\input{regularization_comparison.tex}
-\caption{Comparison of regularization methods using 9 strike prices.}
-\label{fig:regularization}
-\end{figure}
-
 \section{Conclusion}

### 2025-02-12 latex/regularization_comparison.tex
figure

@@
     legend style={font=\tiny, at={(0.02,0.98)}, anchor=north west},
-    xlabel={Underlying Asset Price},
+    xlabel={Underlying Asset Price at Maturity},
     ylabel={Payout},

### 2025-02-12 code/approximation.py

@@ -106,7 +106,7 @@ def example_usage():
     plt.plot(S_test, approx_l2, '--', label='L2 Regularization Approximation', lw=2)
     plt.plot(S_test, approx_l1, '-.', label='L1 Regularization Approximation', lw=2)
     plt.title("Regularization Methods Comparison", fontsize=9)
-    plt.xlabel("Underlying Asset Price", fontsize=8)
+    plt.xlabel("Underlying Asset Price at Maturity", fontsize=8)
     plt.ylabel("Payout", fontsize=8)
     plt.legend(fontsize=8, loc='upper left')
     plt.grid(True, alpha=0.3)
@@ -132,7 +132,7 @@ def example_usage():
     tick label style={font=\tiny},
     title style={font=\small},
     legend style={font=\tiny, at={(0.02,0.98)}, anchor=north west},
-    xlabel={Underlying Asset Price},
+    xlabel={Underlying Asset Price at Maturity},
     ylabel={Payout},
     title={Regularization Methods Comparison}
 ]

### 2025-02-12 latex/article.tex
80 symbols

@@
 The ability to replicate complex financial instruments using simpler, more liquid
-derivatives is a cornerstone of modern financial engineering. Vanilla European options,
-due to their simplicity and widespread availability, serve as ideal building blocks
-for such approximations. This paper introduces an approach to approximating arbitrary
-payout profiles using a combination of these options.
+derivatives is a cornerstone of modern financial engineering. Vanilla European 
+options, due to their simplicity and widespread availability, serve as ideal 
+building blocks for such approximations. This paper introduces an approach to 
+approximating arbitrary payout profiles using a combination of these options.
 
@@
 \subsection{Mathematical Framework}
-Let \( V(S) \) represent the value of a target payout profile as a function of the underlying asset price \( S \).
-We construct an approximation using \( n \) call options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
+Let \( V(S) \) represent the value of a target payout profile as a function of the 
+underlying asset price \( S \). We construct an approximation using \( n \) call 
+options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
 
@@
 
-where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) are
-option weights. The optimal weights are found by solving the regularized least squares
-problem with either L2 (Ridge) or L1 (Lasso) regularization:
+where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) 
+are option weights. The optimal weights are found by solving the regularized least 
+squares problem with either L2 (Ridge) or L1 (Lasso) regularization:
 
@@
 \( S_{\min}, S_{\max} \) define the approximation domain, and \( p \) determines
-the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight distributions,
-while the L1 norm (\(p=1\)) tends to produce sparse solutions by setting some weights
-exactly to zero, which can be beneficial when portfolio simplicity or transaction costs
-are important considerations.
+the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight 
+distributions, while the L1 norm (\(p=1\)) tends to produce sparse solutions by 
+setting some weights exactly to zero, which can be beneficial when portfolio 
+simplicity or transaction costs are important considerations.
 
@@
 
-where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ controls solution smoothness through regularization, and $\mathbf{I}$ denotes the identity matrix.
-Evaluation points $\{S_k\}$ are typically distributed around the current spot price to emphasize approximation accuracy in relevant price regions.
+where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis 
+payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ 
+controls solution smoothness through regularization, and $\mathbf{I}$ denotes the 
+identity matrix. Evaluation points $\{S_k\}$ are typically distributed around the 
+current spot price to emphasize approximation accuracy in relevant price regions. 
 The L1-regularized problem is solved using iterative optimization methods.
@@
 \input{regularization_comparison.tex}
-\caption{Comparison of L1 and L2 regularization}
+\caption{Comparison of L1 and L2 regularization methods for approximating a complex 
+payout profile as a function of the underlying asset price at maturity. The target 
+payout (solid black) combines linear, sinusoidal, and power-law segments. Both L2 
+(dashed) and L1 (dash-dotted) regularization methods achieve good approximation 
+using 9 strike prices, with L1 producing a sparser portfolio.}
 \label{fig:regularization}
@@
 
-Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization approaches in approximating a complex payout profile.
-The target function combines linear, sinusoidal, and power-law segments, presenting a challenging test case.
-Both methods achieve good approximation quality, with L2 regularization providing slightly smoother results and L1 regularization favoring a sparser representation with fewer non-zero option weights.
+Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization 
+approaches in approximating a complex payout profile. The target function combines 
+linear, sinusoidal, and power-law segments, presenting a challenging test case. Both 
+methods achieve good approximation quality, with L2 regularization providing slightly 
+smoother results and L1 regularization favoring a sparser representation with fewer 
+non-zero option weights.
 
@@
 \subsection{Distribution-Based Trading}
-The approximation method enables novel trading strategies that exploit distributional forecasts rather than direct price predictions.
-Traders can hedge against forecasted distribution features, express views on higher moments of price distribution, and implement volatility surface arbitrage strategies through carefully constructed option portfolios.
+The approximation method enables novel trading strategies that exploit distributional 
+forecasts rather than direct price predictions. Traders can hedge against forecasted 
+distribution features, express views on higher moments of price distribution, and 
+implement volatility surface arbitrage strategies through carefully constructed 
+option portfolios.
 
-The key advantage emerges when combining the approximation with distribution forecasts $\mathbb{P}(S_T)$:
+The key advantage emerges when combining the approximation with distribution 
+forecasts $\mathbb{P}(S_T)$:
 
@@
 
-Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payout under forecasted distribution:
+Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payout under 
+forecasted distribution:
 

### 2025-02-12 code/approximation.py
ignore

@@ -1,12 +1,8 @@
 import numpy as np
-from scipy.optimize import minimize
 from typing import Callable, Tuple
-import matplotlib
-matplotlib.use('Agg')  # Добавить в начало файла
-import matplotlib.pyplot as plt
 from sklearn.linear_model import Lasso
 
-def create_basis_functions(strikes: list[float], spot: float) -> list[Callable[[float], float]]:
+def create_basis_functions(strikes: list[float]) -> list[Callable[[float], float]]:
     """Generate call/put payoff functions for given strikes"""
     basis = []
     for K in strikes:
@@ -42,7 +38,7 @@ def approximate_payout(
     S_values = np.linspace(0.5*spot, 1.5*spot, 100)
     
     # Create basis functions (calls/puts)
-    basis = create_basis_functions(strikes, spot)
+    basis = create_basis_functions(strikes)
     
     # Add spot position (lambda*S) to the basis
     basis.append(lambda S: S)  # Lambda term
@@ -88,30 +84,19 @@ def example_usage():
     strikes = [70, 80, 90, 100, 105, 110, 120, 130, 98]
     
     # Run approximation with tighter regularization
-    weights_l2, lambda_l2 = approximate_payout(target, strikes, spot=100, regularization=0.2, method='l2')
-    weights_l1, lambda_l1 = approximate_payout(target, strikes, spot=100, regularization=0.2, method='l1')
+    regularization = 0.05
+    weights_l2, lambda_l2 = approximate_payout(target, strikes, spot=100, regularization=regularization, method='l2')
+    weights_l1, lambda_l1 = approximate_payout(target, strikes, spot=100, regularization=regularization, method='l1')
     
     # Generate comparison data
     S_test = np.linspace(50, 150, 500)
     target_values = target(S_test)
     
-    # Calculate approximated payout
-    basis = create_basis_functions(strikes, spot=100)
+    # Calculate approxi mated payout
+    basis = create_basis_functions(strikes)
     approx_l2 = sum(w*f(S_test) for w, f in zip(weights_l2, basis)) + lambda_l2*S_test
     approx_l1 = sum(w*f(S_test) for w, f in zip(weights_l1, basis)) + lambda_l1*S_test
-    
-    # Create figure with improved styling
-    plt.figure(figsize=(14, 7))
[…]

### 2025-02-12 latex/article.tex
formulas tabs
removed some text
title page positioning
different functions

--- 2025-02-12 latex/article.tex
@@
 \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
-\title{\rule{\textwidth}{4pt}\\
+
+% Remove page number from the first page
+\usepackage{titling}
+\usepackage{geometry}
+
+% Adjust vertical spacing on title page
+\pretitle{\vspace*{2cm}\begin{center}}
+\posttitle{\end{center}\vspace{0.5cm}}
+\preauthor{\begin{center}}
+\postauthor{\end{center}\vspace{0.5cm}}
+\predate{\begin{center}}
+\postdate{\end{center}\vspace{1cm}}
+
+\title{\rule{\textwidth}{4pt}\\[1em]
 \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm]
-Regularized Payout Approximation in Discrete Space}\\[0.2cm]
+Regularized Payout Approximation in Discrete Space}\\[1em]
 \rule{\textwidth}{2pt}}
+
 \author{\small \textbf{Vlad Kochetov} \\
@@
 \begin{document}
+
+% Remove page number from the first page
+\thispagestyle{empty}
 
@@
 \subsection{Mathematical Framework}
-Let \( V(S) \) represent the value of a target payout profile as a function of the underlying asset price \( S \).
-We construct an approximation using \( n \) call options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
+Let \( V(S) \) represent the value of a target payout profile as a function of the 
+underlying asset price \( S \). We construct an approximation using \( n \) call 
+options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
 
 \begin{equation}
-V(S) \approx \lambda S + \sum_{i=1}^{n} \alpha_i C(S, K_i) + \sum_{j=1}^{m} \beta_j P(S, K_j)
+V(S) \approx \lambda S + 
+    \sum_{i=1}^{n} \alpha_i C(S, K_i) + 
+    \sum_{j=1}^{m} \beta_j P(S, K_j)
 \end{equation}
 
-where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) are
-option weights. The optimal weights are found by solving the regularized least squares
-problem with either L2 (Ridge) or L1 (Lasso) regularization:
+where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) 
+are option weights. The optimal weights are found by solving the regularized least 
+squares problem with either L2 (Ridge) or L1 (Lasso) regularization:
 
 \begin{equation}
-\min_{\boldsymbol{\theta}} \int_{S_{\min}}^{S_{\max}} \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + \gamma \|\boldsymbol{\theta}\|_p^p
+\min_{\boldsymbol{\theta}} 
+    \int_{S_{\min}}^{S_{\max}} 
+        \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
+    \gamma \|\boldsymbol{\theta}\|_p^p
 \end{equation}
@@
 \begin{equation}
-\boldsymbol{\theta}^* = \argmin_{\boldsymbol{\theta}} \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + \gamma \|\boldsymbol{\theta}\|_p^p
+\boldsymbol{\theta}^* = 
+    \argmin_{\boldsymbol{\theta}} 
+        \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + 
+        \gamma \|\boldsymbol{\theta}\|_p^p
 \end{equation}
@@
 \begin{equation}
-\boldsymbol{\theta}^* = (\mathbf{A}^\top \mathbf{A} + \gamma \mathbf{I})^{-1} \mathbf{A}^\top \mathbf{b}
+\boldsymbol{\theta}^* = 
+    (\mathbf{A}^\top \mathbf{A} + \gamma \mathbf{I})^{-1} 
+    \mathbf{A}^\top \mathbf{b}
 \end{equation}
 
-where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ controls solution smoothness through regularization, and $\mathbf{I}$ denotes the identity matrix.
-Evaluation points $\{S_k\}$ are typically distributed around the current spot price to emphasize approximation accuracy in relevant price regions.
+where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis 
+payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ 
+controls solution smoothness through regularization, and $\mathbf{I}$ denotes the 
+identity matrix. Evaluation points $\{S_k\}$ are typically distributed around the 
+current spot price to emphasize approximation accuracy in relevant price regions. 
 The L1-regularized problem is solved using iterative optimization methods.
@@
 
-Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization approaches in approximating a complex payout profile.
-The target function combines linear, sinusoidal, and power-law segments, presenting a challenging test case.
-Both methods achieve good approximation quality, with L2 regularization providing slightly smoother results and L1 regularization favoring a sparser representation with fewer non-zero option weights.
+Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization 
+approaches in approximating a complex payout profile. The target function combines 
+different types of functions, presenting a challenging test case. Both 
+methods achieve good approximation quality, with L2 regularization providing slightly 
+smoother results and L1 regularization favoring a sparser representation with fewer 
+non-zero option weights.
 
@@
 \subsection{Distribution-Based Trading}
-The approximation method enables novel trading strategies that exploit distributional forecasts rather than direct price predictions.
-Traders can hedge against forecasted distribution features, express views on higher moments of price distribution, and implement volatility surface arbitrage strategies through carefully constructed option portfolios.
+The approximation method enables novel trading strategies that exploit distributional 
+forecasts rather than direct price predictions. Traders can hedge against forecasted 
+distribution features, express views on higher moments of price distribution, and 
+implement volatility surface arbitrage strategies through carefully constructed 
+option portfolios.
 
-The key advantage emerges when combining the approximation with distribution forecasts $\mathbb{P}(S_T)$:
+The key advantage emerges when combining the approximation with distribution 
+forecasts $\mathbb{P}(S_T)$:
 
 \begin{equation}
-\mathbb{E}[V(S_T)] = \int_{0}^{\infty} V(S) \mathbb{P}(S_T = S) dS
+\mathbb{E}[V(S_T)] = 
+    \int_{0}^{\infty} 
+        V(S) \mathbb{P}(S_T = S) dS
 \end{equation}
 
-Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payout under forecasted distribution:
+Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payout under 
+forecasted distribution:
 
 \begin{equation}
-\boldsymbol{\theta}^* = \argmax_{\boldsymbol{\theta}} \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - \lambda \text{Var}\left(\hat{V}(S_T;\boldsymbol{\theta})\right)
+\boldsymbol{\theta}^* = 
+    \argmax_{\boldsymbol{\theta}} 
+        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
+        \lambda \text{Var}\left(\hat{V}(S_T;\boldsymbol{\theta})\right)
 \end{equation}

### 2025-02-12 code/approximation.py
unused call-put parity

@@ -2,14 +2,20 @@ import numpy as np
 from typing import Callable, Tuple
 from sklearn.linear_model import Lasso
 
+
+USE_CALL_PUT_PARITY = False
+regularization = 0.1
+
 def create_basis_functions(strikes: list[float]) -> list[Callable[[float], float]]:
-    """Generate call/put payoff functions for given strikes"""
+    """Generate call payoff functions and spot position using put-call parity"""
     basis = []
     for K in strikes:
-        # Call option payoff: max(S - K, 0)
+        # Only call options needed (puts can be expressed via calls + spot)
         basis.append(lambda S, K=K: np.maximum(S - K, 0))
-        # Put option payoff: max(K - S, 0) 
-        basis.append(lambda S, K=K: np.maximum(K - S, 0))
+        if not USE_CALL_PUT_PARITY:
+            # Put option payoff: max(K - S, 0) 
+            basis.append(lambda S, K=K: np.maximum(K - S, 0))
+
     return basis
 
 def approximate_payout(
@@ -40,8 +46,9 @@ def approximate_payout(
     # Create basis functions (calls/puts)
     basis = create_basis_functions(strikes)
     
-    # Add spot position (lambda*S) to the basis
-    basis.append(lambda S: S)  # Lambda term
+    # Add spot position to the basis if using put-call parity
+    if USE_CALL_PUT_PARITY:
+        basis.append(lambda S: S)  # Spot position
     
     # Build design matrix
     A = np.array([[f(S) for f in basis] for S in S_values])
@@ -55,15 +62,19 @@ def approximate_payout(
             rcond=None
         )[0]
     elif method == 'l1':
-        # L1 регуляризация с использованием Lasso
+        # L1 regularization using Lasso
         model = Lasso(alpha=regularization, fit_intercept=False, max_iter=10000)
         model.fit(A, b)
         solution = model.coef_
     else:
         raise ValueError("Invalid method. Use 'l1' or 'l2'")
     
-    # Split solution into options weights and lambda
-    return solution[:-1], solution[-1]
+    if USE_CALL_PUT_PARITY:
+        # Split solution into options weights and lambda
+        return solution[:-1], solution[-1]
+    else:
[…]

### 2025-02-14 latex/article.tex
Carr-Madan reference

@@
 \section{Literature Review}
+The theoretical foundations of option portfolio optimization were established by 
+\cite{Carr01012001}, who demonstrated the theoretical possibility of replicating 
+arbitrary payout functions through continuous strike spaces. While their approach 
+provides elegant closed-form solutions in continuous market settings, three fundamental 
+limitations hinder practical implementation: the discrete availability of strike prices 
+in real markets, liquidity constraints, non-negligible transaction costs scaling with 
+portfolio complexity, and numerical stability challenges in finite difference implementations. 
+Proposed method addresses these limitations through regularization techniques and 
+discrete optimization methods tailored for real-world trading environments, while 
+preserving the theoretical elegance of the original framework.
 

### 2025-02-18 latex/article.tex
model assumptions

--- 2025-02-12 latex/article.tex
@@
 \usepackage{graphicx}
-\usepackage{cite}
+\usepackage{natbib}
 \usepackage{hyperref}
@@
 \section{Literature Review}
+The theoretical foundations of option portfolio optimization were established in the work of 
+\citep{Carr01012001}, which demonstrated the theoretical possibility of replicating 
+arbitrary payout functions through continuous strike spaces. While this approach 
+provides elegant closed-form solutions in continuous market settings, several fundamental 
+limitations affect practical implementation: the discrete availability of strike prices 
+in real markets, liquidity constraints, non-negligible transaction costs scaling with 
+portfolio complexity, and numerical stability challenges in finite difference implementations. 
+The proposed method addresses these limitations through regularization techniques and 
+discrete optimization methods tailored for real-world trading environments, while 
+preserving the theoretical elegance of the original framework.
 
@@
 \subsection{Model Assumptions}
+The proposed approximation framework relies on several key assumptions:
+
+\begin{enumerate}
+    \item \textbf{Discrete Strike Space:} The model operates in a discrete strike price space 
+    $\{K_i\}_{i=1}^n$, reflecting real market conditions where options are available only 
+    at specific strikes.
+
+    \item \textbf{Local Approximation Region:} The approximation focuses on a finite price 
+    interval around the current spot price $[S_{\min}, S_{\max}]$, where $S_{\min}$ and $S_{\max}$ 
+    are chosen to ensure sufficient coverage of the relevant price region.
+
+    \item \textbf{European-Style Options:} The framework utilizes European-style vanilla 
+    options exclusively, avoiding the complexity of early exercise features present in 
+    American options.
+
+    \item \textbf{Static Replication:} The model assumes a static replication approach, 
+    where the portfolio weights remain constant until maturity. Dynamic rebalancing effects 
+    are not considered in the basic framework.
+
+    \item \textbf{Put-Call Parity Flexibility:} The implementation allows for two 
+    alternative approaches:
+    \begin{itemize}
+        \item Direct use of both calls and puts as separate instruments
+        \item Expressing puts through calls and spot positions using put-call parity
+    \end{itemize}
+    This flexibility enables optimization of the portfolio structure based on market 
+    conditions and transaction costs.
+\end{enumerate}
+
+The numerical implementation discretizes the approximation domain into a finite set of 
+evaluation points. The number of discretization points is chosen to balance computational 
+efficiency with approximation accuracy.
 
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{apalike}
 \bibliography{references}

### 2025-02-18 latex/article.tex
costs are not problem

@@
 setting some weights exactly to zero, which can be beneficial when portfolio 
-simplicity or transaction costs are important considerations.
+simplicity is important consideration.
 

### 2025-02-18 code/distrofit_2.py
eng comments

@@ -73,26 +73,26 @@ class DistributionToPayout:
             plt.savefig(save_path, dpi=150)
         plt.show()
 
-# Обновлённый пример использования
+# Updated usage example
 if __name__ == "__main__":
-    # Параметры смеси гауссианов
+    # Gaussian mixture parameters
     def gaussian_mixture(x, mu1=1.0, sigma1=0.5, mu2=3.0, sigma2=0.8, weight=0.3):
         return (weight * np.exp(-(x-mu1)**2/(2*sigma1**2)) / (sigma1*np.sqrt(2*np.pi)) 
                 + (1-weight) * np.exp(-(x-mu2)**2/(2*sigma2**2)) / (sigma2*np.sqrt(2*np.pi)))
 
-    # Создаем распределение на основе смеси гауссианов
+    # Create distribution based on Gaussian mixture
     price_bins = np.linspace(-0.1, 5.0, 101)
     bin_centers = (price_bins[1:] + price_bins[:-1])/2
     probs = gaussian_mixture(bin_centers)
-    probs /= probs.sum()  # Нормализуем
+    probs /= probs.sum()  # Normalize
     
-    # Инициализируем преобразователь
+    # Initialize converter
     converter = DistributionToPayout(price_bins, probs)
     
-    # Визуализация
+    # Visualization
     converter.plot_distribution(save_path="gaussian_mixture_payout.png")
     
-    # Тестируем функцию
+    # Test function
     test_prices = [0.5, 1.0, 2.0, 3.0, 4.0]
     for price in test_prices:
         print(f"Payout at {price:.2f}%: {converter.get_payout_function()(price):.4f}")

### 2025-02-19 latex/article.tex
alternative

@@
 
-    \item \textbf{Put-Call Parity Flexibility:} The implementation allows for two 
-    alternative approaches:
-    \begin{itemize}
-        \item Direct use of both calls and puts as separate instruments
-        \item Expressing puts through calls and spot positions using put-call parity
-    \end{itemize}
+    \item \textbf{Put-Call Parity Flexibility:} The implementation supports both direct 
+    use of calls and puts as separate instruments, as well as expressing puts through 
+    calls and spot positions using put-call parity. This approach provides flexibility 
+    in portfolio construction while maintaining mathematical equivalence.
     This flexibility enables optimization of the portfolio structure based on market 
-    conditions and transaction costs.
+    conditions.
 \end{enumerate}
@@
 are option weights. The optimal weights are found by solving the regularized least 
-squares problem with either L2 (Ridge) or L1 (Lasso) regularization:
+squares problem with L2 (Ridge) regularization:
 
@@
         \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
-    \gamma \|\boldsymbol{\theta}\|_p^p
+    \gamma \|\boldsymbol{\theta}\|_2^2
 \end{equation}
@@
 where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
-the position weights, \( \gamma \) is the regularization parameter, 
-\( S_{\min}, S_{\max} \) define the approximation domain, and \( p \) determines
-the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight 
-distributions, while the L1 norm (\(p=1\)) tends to produce sparse solutions by 
-setting some weights exactly to zero, which can be beneficial when portfolio 
-simplicity is important consideration.
+the position weights, \( \gamma \) is the regularization parameter, and 
+\( S_{\min}, S_{\max} \) define the approximation domain. The L2 norm promotes 
+smoother weight distributions, providing stability to the solution.
 
-Discretizing the integral and using matrix notation, we solve:
+Discretizing the integral and using matrix notation, we obtain:
 
@@
         \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + 
-        \gamma \|\boldsymbol{\theta}\|_p^p
+        \gamma \|\boldsymbol{\theta}\|_2^2
 \end{equation}
@@
 
-\subsection{Numerical Implementation}
-The discrete optimization problem with L2 regularization has a closed-form solution:
+This quadratic optimization problem admits an analytical solution:
 \begin{equation}
@@
 
-where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis 
-payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ 
-controls solution smoothness through regularization, and $\mathbf{I}$ denotes the 
-identity matrix. Evaluation points $\{S_k\}$ are typically distributed around the 
-current spot price to emphasize approximation accuracy in relevant price regions. 
-The L1-regularized problem is solved using iterative optimization methods.
+\subsection{Alternative Loss Functions}
+While the standard L2 loss function provides analytical tractability, alternative 
+formulations may better reflect trading objectives. Two notable generalizations are:
+
+\begin{enumerate}
+    \item \textbf{L1 Regularization (Lasso):} Replacing L2 regularization term with L1 norm:
+    \begin{equation}
+        L(\boldsymbol{\theta}) = 
+            \int_{S_{\min}}^{S_{\max}} 
+                \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
+            \gamma \|\boldsymbol{\theta}\|_1
+    \end{equation}
+    This formulation tends to produce sparse solutions by setting some weights exactly 
+    to zero, which can be beneficial when portfolio simplicity is important consideration.
+
+    \item \textbf{Weighted Error Function:} Incorporating target function magnitude 
+    into the error term:
+    \begin{equation}
+        L(\boldsymbol{\theta}) = 
+            \int_{S_{\min}}^{S_{\max}} 
+                V(S) \Big| V(S) - \hat{V}(S;\boldsymbol{\theta}) \Big| dS + 
+            \gamma \|\boldsymbol{\theta}\|_p^p
+    \end{equation}
+    This formulation provides error weighting proportional to the target payout magnitude, 
+    offering economic interpretation well-aligned with trading objectives. Furthermore, it 
+    naturally enhances focus on regions with significant payout values, making it particularly 
+    suitable for practical applications.
+\end{enumerate}
+
+However, these generalizations lose the analytical tractability of the L2 case, 
+requiring numerical optimization methods for solution.
+
+\subsection{Numerical Implementation}
+The implementation leverages the analytical solution derived in the Mathematical Framework 
+section for L2-regularized problems. For L1 regularization and alternative loss functions, 
+numerical optimization methods are employed.
 

### 2025-02-19 latex/article.tex
payoff

@@
 \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm]
-Regularized Payout Approximation in Discrete Space}\\[1em]
+Regularized Payoff Approximation in Discrete Space}\\[1em]
 \rule{\textwidth}{2pt}}
@@
 \begin{abstract}
-This paper explores the methodology for approximating complex payout profiles using a
+This paper explores the methodology for approximating complex payoff profiles using a
 combination of vanilla European options. The mathematical framework is presented that
-allows for the decomposition of arbitrary payout structures into a series of call and
+allows for the decomposition of arbitrary payoff structures into a series of call and
 put options with varying strike prices. The approach is validated through numerical
 examples and practical applications in financial engineering. The results demonstrate
-the effectiveness of this method in replicating complex payouts.
+the effectiveness of this method in replicating complex payoffs.
 \end{abstract}
@@
         Vanilla Options, 
-        Payout Profile, 
+        Payoff Profile, 
         Financial Engineering, 
@@
 building blocks for such approximations. This paper introduces an approach to 
-approximating arbitrary payout profiles using a combination of these options.
+approximating arbitrary payoff profiles using a combination of these options.
 
@@
 \citep{Carr01012001}, which demonstrated the theoretical possibility of replicating 
-arbitrary payout functions through continuous strike spaces. While this approach 
+arbitrary payoff functions through continuous strike spaces. While this approach 
 provides elegant closed-form solutions in continuous market settings, several fundamental 
@@
 \subsection{Mathematical Framework}
-Let \( V(S) \) represent the value of a target payout profile as a function of the 
+Let \( V(S) \) represent the value of a target payoff profile as a function of the 
 underlying asset price \( S \). We construct an approximation using \( n \) call 
@@
 evaluated at discrete price points \( \{S_k\}_{k=1}^N \), and \( \mathbf{b} \) is
-the vector of target payout values.
+the vector of target payoff values.
 
@@
     \end{equation}
-    This formulation provides error weighting proportional to the target payout magnitude, 
+    This formulation provides error weighting proportional to the target payoff magnitude, 
     offering economic interpretation well-aligned with trading objectives. Furthermore, it 
-    naturally enhances focus on regions with significant payout values, making it particularly 
+    naturally enhances focus on regions with significant payoff values, making it particularly 
     suitable for practical applications.
@@
 Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization 
-approaches in approximating a complex payout profile. The target function combines 
+approaches in approximating a complex payoff profile. The target function combines 
 different types of functions, presenting a challenging test case. Both 
@@
 
-Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payout under 
+Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payoff under 
 forecasted distribution:

### 2025-02-19 latex/regularization_comparison.tex
ignore
unused call-put parity
payoff

--- 2025-02-12 latex/regularization_comparison.tex
@@
     legend style={font=\tiny, at={(0.02,0.98)}, anchor=north west},
-    xlabel={Underlying Asset Price},
-    ylabel={Payout},
+    xlabel={Underlying Asset Price at Maturity},
+    ylabel={Payoff},
     title={Regularization Methods Comparison}
@@
 \addplot[thick, black] table[x index=0,y index=1] {regularization_comparison.dat};
-\addlegendentry{Target Payout}
+\addlegendentry{Target Payoff}
 
 \addplot[thick, dashed, red] table[x index=0,y index=2] {regularization_comparison.dat};
-\addlegendentry{L2 Regularization Approximation}
+\addlegendentry{L2 Approximation($\gamma=0.10$)}
 
 \addplot[thick, dashdotted, blue] table[x index=0,y index=3] {regularization_comparison.dat};
-\addlegendentry{L1 Regularization Approximation}
+\addlegendentry{L1 Approximation($\gamma=0.10$)}
 

### 2025-02-19 code/approximation.py

@@ -18,18 +18,18 @@ def create_basis_functions(strikes: list[float]) -> list[Callable[[float], float
 
     return basis
 
-def approximate_payout(
-    target_payout: Callable[[float], float],
+def approximate_payoff(
+    target_payoff: Callable[[float], float],
     strikes: list[float],
     spot: float,
     regularization: float = 0.05,
     method: str = 'l2'
 ) -> Tuple[np.ndarray, float]:
     """
-    Approximate target payout using vanilla options
+    Approximate target payoff using vanilla options
     
     Args:
-        target_payout: Function of S (spot price) to approximate
+        target_payoff: Function of S (spot price) to approximate
         strikes: Available strike prices
         spot: Current spot price
         regularization: L2 regularization parameter
@@ -52,7 +52,7 @@ def approximate_payout(
     
     # Build design matrix
     A = np.array([[f(S) for f in basis] for S in S_values])
-    b = np.array([target_payout(S) for S in S_values])
+    b = np.array([target_payoff(S) for S in S_values])
     
     if method == 'l2':
         # Solve regularized least squares
@@ -77,8 +77,8 @@ def approximate_payout(
         return solution, 0.0
 
 def example_usage():
-    """Demonstrate approximation of complex payout structure"""
-    # Define complex target payout function
+    """Demonstrate approximation of complex payoff structure"""
+    # Define complex target payoff function
     def target(S):
         return np.where(
             S < 80,
@@ -95,14 +95,14 @@ def example_usage():
     strikes = [70, 80, 90, 100, 105, 110, 120, 130, 98]
     
     # Run approximation with tighter regularization
-    weights_l2, lambda_l2 = approximate_payout(target, strikes, spot=100, regularization=regularization, method='l2')
-    weights_l1, lambda_l1 = approximate_payout(target, strikes, spot=100, regularization=regularization, method='l1')
+    weights_l2, lambda_l2 = approximate_payoff(target, strikes, spot=100, regularization=regularization, method='l2')
+    weights_l1, lambda_l1 = approximate_payoff(target, strikes, spot=100, regularization=regularization, method='l1')
     
     # Generate comparison data
     S_test = np.linspace(50, 150, 500)
     target_values = target(S_test)
     
-    # Calculate approximated payout
+    # Calculate approximated payoff
[…]

### 2025-02-19 code/distrofit.py

@@ -3,105 +3,101 @@ from typing import Callable
 import plotly.graph_objects as go
 from plotly.subplots import make_subplots
 
-class DistributionToPayout:
+class DistributionToPayoff:
     """
-    Converts probability distribution forecast to payout function
+    Converts probability distribution forecast to payoff function
     
-    Parameters:
-        bins (np.ndarray): Array of bin edges (N+1 elements)
-        probabilities (np.ndarray): Probability for each bin (N elements)
-        payout_scale (float): Scaling factor for payout amounts
+    Args:
+        price_bins (list[float]): List of price bin edges
+        probabilities (list[float]): Probability for each bin
+        payoff_scale (float): Scaling factor for payoff amounts
     """
+    
     def __init__(
         self,
-        bins: np.ndarray,
-        probabilities: np.ndarray,
-        payout_scale: float = 100.0
+        price_bins: list[float],
+        probabilities: list[float],
+        payoff_scale: float = 100.0
     ):
-        self.bins = bins
+        self.price_bins = price_bins
         self.probabilities = probabilities
-        self.payout_scale = payout_scale
+        self.payoff_scale = payoff_scale
         
-        # Validate inputs
-        assert len(bins) == len(probabilities) + 1, "Invalid bins-probabilities shape"
-        assert np.isclose(probabilities.sum(), 1.0), "Probabilities must sum to 1"
+        if len(price_bins) != len(probabilities) + 1:
+            raise ValueError("Length of price_bins must be one more than probabilities")
+    
+    def get_payoff_function(self) -> Callable[[float], float]:
+        """Create piecewise constant payoff function"""
         
-    def get_payout_function(self) -> Callable[[float], float]:
-        """Create piecewise constant payout function"""
-        # Calculate midpoints for each bin
-        midpoints = (self.bins[1:] + self.bins[:-1]) / 2
+        # Ensure probabilities sum to 1
+        self.probabilities = np.array(self.probabilities) / sum(self.probabilities)
         
-        # Calculate payout weights: inverse probability weighting
-        weights = self.payout_scale * (1 / (self.probabilities + 1e-8))
+        # Calculate payoff weights: inverse probability weighting
+        weights = self.payoff_scale * (1 / (self.probabilities + 1e-8))
         
[…]

### 2025-02-19 code/distrofit_2.py

@@ -2,97 +2,98 @@ import numpy as np
 from typing import Callable
 import matplotlib.pyplot as plt
 
-class DistributionToPayout:
+class DistributionToPayoff:
     """
-    Converts probability distribution forecast to payout function
+    Converts probability distribution forecast to payoff function
     
-    Parameters:
-        bins (np.ndarray): Array of bin edges (N+1 elements)
-        probabilities (np.ndarray): Probability for each bin (N elements)
-        payout_scale (float): Scaling factor for payout amounts
+    Args:
+        price_bins (list[float]): List of price bin edges
+        probabilities (list[float]): Probability for each bin
+        payoff_scale (float): Scaling factor for payoff amounts
     """
+    
     def __init__(
         self,
-        bins: np.ndarray,
-        probabilities: np.ndarray,
-        payout_scale: float = 100.0
+        price_bins: list[float],
+        probabilities: list[float],
+        payoff_scale: float = 100.0
     ):
-        self.bins = bins
+        self.price_bins = price_bins
         self.probabilities = probabilities
-        self.payout_scale = payout_scale
+        self.payoff_scale = payoff_scale
         
-        # Validate inputs
-        assert len(bins) == len(probabilities) + 1, "Invalid bins-probabilities shape"
-        assert np.isclose(probabilities.sum(), 1.0), "Probabilities must sum to 1"
+        if len(price_bins) != len(probabilities) + 1:
+            raise ValueError("Length of price_bins must be one more than probabilities")
+    
+    def get_payoff_function(self) -> Callable[[float], float]:
+        """Create piecewise constant payoff function"""
         
-    def get_payout_function(self) -> Callable[[float], float]:
-        """Create piecewise constant payout function"""
-        # Calculate midpoints for each bin
-        midpoints = (self.bins[1:] + self.bins[:-1]) / 2
+        # Ensure probabilities sum to 1
+        self.probabilities = np.array(self.probabilities) / sum(self.probabilities)
         
-        # Calculate payout weights: inverse probability weighting
-        weights = self.payout_scale * (1 / (self.probabilities + 1e-8))
+        # Calculate payoff weights: inverse probability weighting
[…]

### 2025-02-19 latex/article.tex
why it's cool

@@
 approximating arbitrary payoff profiles using a combination of these options.
+
+The traditional approach to financial modeling often relies heavily on assumptions about
+the underlying price distribution, with the normal distribution being the most common choice
+due to its mathematical tractability. However, empirical evidence consistently shows that
+market price distributions exhibit significant deviations from normality \citep{Pokharel2024},
+particularly in the form of heavy tails and higher moments that cannot be captured by simple
+parametric models. This mismatch between theoretical assumptions and market reality can lead to
+systematic pricing errors and risk underestimation.
+
+Presented approach addresses these limitations by embracing the stochastic nature of markets
+without imposing restrictive distributional assumptions. Instead of attempting to fit
+market behavior into predetermined probability distributions as in \citep{Kuang2023}, 
+this paper proposes a framework that can accommodate any empirically observed distribution. This 
+distribution-free modeling approach acknowledges the complex, non-Gaussian nature of 
+market price movements, which often exhibit fat tails and asymmetric behavior. It allows 
+for direct incorporation of empirical distribution forecasts, enabling more accurate risk 
+assessment and pricing.
+Furthermore, the framework provides a flexible mechanism for extracting value from market
+inefficiencies without relying on specific distributional assumptions, while being able
+to adapt to changing market conditions and regime shifts that affect the shape of price
+distributions.
+
+The proposed methodology bridges the gap between theoretical option pricing models
+and observed market behavior by providing a practical framework for implementing
+distribution-based trading strategies. By focusing on distribution forecasting
+rather than point predictions, traders can develop more robust strategies that
+account for the full spectrum of possible market outcomes.
 

### 2025-02-19 latex/article.tex
idea sources

@@
 
-Presented approach addresses these limitations by embracing the stochastic nature of markets
+The presented approach addresses these limitations by embracing the stochastic nature of markets
 without imposing restrictive distributional assumptions. Instead of attempting to fit
-market behavior into predetermined probability distributions as in \citep{Kuang2023}, 
-this paper proposes a framework that can accommodate any empirically observed distribution. This 
-distribution-free modeling approach acknowledges the complex, non-Gaussian nature of 
-market price movements, which often exhibit fat tails and asymmetric behavior. It allows 
-for direct incorporation of empirical distribution forecasts, enabling more accurate risk 
-assessment and pricing.
+market behavior into predetermined probability distributions as in \citep{Kuang2023} and 
+\citep{Li2023}, this paper proposes a framework that can accommodate any empirically 
+observed distribution. This distribution-free modeling approach acknowledges the complex, 
+non-Gaussian nature of market price movements, which often exhibit fat tails and 
+asymmetric behavior. It allows for direct incorporation of empirical distribution forecasts, 
+enabling more accurate risk assessment and pricing.
 Furthermore, the framework provides a flexible mechanism for extracting value from market
@@
 portfolio complexity, and numerical stability challenges in finite difference implementations.
+
+The idea of modeling complete distributions rather than point estimates was inspired by recent 
+advances in time series forecasting, particularly the work of \citep{ansari2024chronos}, which 
+demonstrated the effectiveness of distribution-based predictions in capturing complex temporal 
+patterns. While tail risk hedging has been a fundamental concept since \citep{BlackScholes1973}, 
+where options were primarily used for downside protection, our approach extends this by 
+considering the entire distribution shape in portfolio construction. Unlike traditional methods 
+that focus solely on tail events, we propose a comprehensive framework that models and exploits 
+the complete probability distribution of asset returns.
+
 The proposed method addresses these limitations through regularization techniques and 

### 2025-02-19 code/approximation.py
non-neg payoff

@@ -89,7 +89,7 @@ def example_usage():
                               0.8*(120 - S)**1.5,
                               0)
                     )
-        )
+        ) + 15
     
     # Available strikes (limited set)
     strikes = [70, 80, 90, 100, 105, 110, 120, 130, 98]

### 2025-02-19 latex/article.tex
weighted

@@
 
+\begin{figure}[htbp]
+\centering
+\input{weighted_loss.tex}
+\caption{Weighted Error Method Performance}
+\label{fig:weighted}
+\end{figure}
+
+Figure~\ref{fig:weighted} illustrates the performance of the weighted error method, 
+which places greater emphasis on accurately approximating regions with larger payoff 
+values. This approach is particularly useful when the economic significance of errors 
+varies with the magnitude of the target payoff, providing a more practical solution 
+for trading applications.
+
 \section{Results}

### 2025-02-19 latex/weighted_loss.tex
weighted

\begin{tikzpicture}
\begin{axis}[
    width=0.9\textwidth,
    height=6cm,
    grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
    xlabel style={font=\tiny},
    ylabel style={font=\tiny},
    tick label style={font=\tiny},
    title style={font=\small},
    legend style={font=\tiny, at={(0.02,0.98)}, anchor=north west},
    xlabel={Underlying Asset Price at Maturity},
    ylabel={Payoff},
    title={Weighted Error Method Comparison}
]

\addplot[thick, black] table[x index=0,y index=1] {weighted_loss.dat};
\addlegendentry{Target Payoff}

\addplot[thick, dotted, green!50!black] table[x index=0,y index=2] {weighted_loss.dat};
\addlegendentry{Weighted Error ($\gamma=0.10$)}

\end{axis}
\end{tikzpicture}

### 2025-02-19 code/approximation.py

@@ -1,6 +1,7 @@
 import numpy as np
 from typing import Callable, Tuple
 from sklearn.linear_model import Lasso
+from scipy.optimize import minimize
 
 
 USE_CALL_PUT_PARITY = False
@@ -18,6 +19,25 @@ def create_basis_functions(strikes: list[float]) -> list[Callable[[float], float
 
     return basis
 
+def weighted_error_objective(weights: np.ndarray, A: np.ndarray, b: np.ndarray, gamma: float) -> float:
+    """
+    Compute weighted error objective function
+    
+    Args:
+        weights: Current solution vector
+        A: Design matrix
+        b: Target values
+        gamma: Regularization parameter
+        
+    Returns:
+        Weighted error value
+    """
+    pred = A @ weights
+    error = np.abs(pred - b)
+    weighted_error = np.sum(np.abs(b) * error)
+    regularization = gamma * np.sum(np.abs(weights))
+    return weighted_error + regularization
+
 def approximate_payoff(
     target_payoff: Callable[[float], float],
     strikes: list[float],
@@ -32,8 +52,8 @@ def approximate_payoff(
         target_payoff: Function of S (spot price) to approximate
         strikes: Available strike prices
         spot: Current spot price
-        regularization: L2 regularization parameter
-        method: Method of regularization ('l2' or 'l1')
+        regularization: Regularization parameter
+        method: Method of regularization ('l2', 'l1', or 'weighted')
         
     Returns:
         Tuple (weights, lambda) where:
@@ -66,8 +86,19 @@ def approximate_payoff(
         model = Lasso(alpha=regularization, fit_intercept=False, max_iter=10000)
         model.fit(A, b)
         solution = model.coef_
+    elif method == 'weighted':
+        # Weighted error optimization
+        x0 = np.zeros(A.shape[1])
+        result = minimize(
+            weighted_error_objective,
+            x0,
+            args=(A, b, regularization),
+            method='SLSQP',
+            options={'maxiter': 1000}
+        )
+        solution = result.x
     else:
-        raise ValueError("Invalid method. Use 'l1' or 'l2'")
+        raise ValueError("Invalid method. Use 'l1', 'l2', or 'weighted'")
     
[…]

### 2025-02-19 latex/article.tex
MAPE comparison

@@
 
+\input{method_comparison.tex}
+
+Table~\ref{tab:method_comparison} presents a comparative analysis of the three regularization 
+methods across different regularization parameters ($\gamma$). The Mean Absolute Percentage 
+Error (MAPE) is used as the primary metric for comparison, providing a scale-independent 
+measure of approximation accuracy. Lower MAPE values indicate better approximation quality.
+
+The results demonstrate that:
+\begin{itemize}
+    \item L2 regularization provides consistent performance across different $\gamma$ values,
+    showing good stability in the approximation.
+    \item L1 regularization achieves comparable accuracy while promoting sparser solutions,
+    which can be advantageous for portfolio implementation.
+    \item The weighted error method shows improved accuracy in regions with larger payoff
+    values, as reflected in its MAPE scores, particularly for moderate regularization values.
+\end{itemize}
+
 \section{Conclusion}

### 2025-02-19 code/approximation.py

@@ -2,10 +2,21 @@ import numpy as np
 from typing import Callable, Tuple
 from sklearn.linear_model import Lasso
 from scipy.optimize import minimize
+import os
 
 
 USE_CALL_PUT_PARITY = False
 regularization = 0.1
+
+# Define paths
+BASE_DIR = os.path.dirname(os.path.dirname(os.path.abspath(__file__)))
+LATEX_DIR = os.path.join(BASE_DIR, "latex")
+
+def ensure_dir(file_path):
+    """Create directory if it doesn't exist"""
+    directory = os.path.dirname(file_path)
+    if not os.path.exists(directory):
+        os.makedirs(directory)
 
 def create_basis_functions(strikes: list[float]) -> list[Callable[[float], float]]:
     """Generate call payoff functions and spot position using put-call parity"""
@@ -107,6 +118,68 @@ def approximate_payoff(
         # Return all weights and 0 for lambda since no spot position used
         return solution, 0.0
 
+def calculate_mape(y_true: np.ndarray, y_pred: np.ndarray) -> float:
+    """Calculate Mean Absolute Percentage Error"""
+    return np.mean(np.abs((y_true - y_pred) / y_true)) * 100
+
+def generate_comparison_table(
+    target_payoff: Callable[[float], float],
+    strikes: list[float],
+    spot: float,
+    regularization_values: list[float]
+) -> None:
+    """Generate performance comparison table for different regularization values"""
+    # Generate evaluation points
+    S_test = np.linspace(50, 150, 500)
+    target_values = target_payoff(S_test)
+    
+    # Initialize results storage
+    results = []
+    
+    for reg in regularization_values:
+        # Calculate approximations for each method
+        weights_l2, lambda_l2 = approximate_payoff(target_payoff, strikes, spot, reg, 'l2')
+        weights_l1, lambda_l1 = approximate_payoff(target_payoff, strikes, spot, reg, 'l1')
+        weights_weighted, lambda_weighted = approximate_payoff(target_payoff, strikes, spot, reg, 'weighted')
+        
+        # Calculate approximated values
+        basis = create_basis_functions(strikes)
+        approx_l2 = sum(w*f(S_test) for w, f in zip(weights_l2, basis))
+        approx_l1 = sum(w*f(S_test) for w, f in zip(weights_l1, basis))
[…]

### 2025-02-19 latex/article.tex
MAE metric

@@
 Table~\ref{tab:method_comparison} presents a comparative analysis of the three regularization 
-methods across different regularization parameters ($\gamma$). The Mean Absolute Percentage 
-Error (MAPE) is used as the primary metric for comparison, providing a scale-independent 
-measure of approximation accuracy. Lower MAPE values indicate better approximation quality.
+methods across different regularization parameters ($\gamma$). The Mean Absolute Error (MAE) 
+is used as the primary metric for comparison, providing a direct measure of approximation accuracy 
+in absolute terms. Lower MAE values indicate better approximation quality.
 
@@
     \item The weighted error method shows improved accuracy in regions with larger payoff
-    values, as reflected in its MAPE scores, particularly for moderate regularization values.
+    values, as reflected in its MAE scores, particularly for moderate regularization values.
 \end{itemize}

### 2025-02-19 code/approximation.py

@@ -118,9 +118,9 @@ def approximate_payoff(
         # Return all weights and 0 for lambda since no spot position used
         return solution, 0.0
 
-def calculate_mape(y_true: np.ndarray, y_pred: np.ndarray) -> float:
-    """Calculate Mean Absolute Percentage Error"""
-    return np.mean(np.abs((y_true - y_pred) / y_true)) * 100
+def calculate_mae(y_true: np.ndarray, y_pred: np.ndarray) -> float:
+    """Calculate Mean Absolute Error"""
+    return np.mean(np.abs(y_true - y_pred))
 
 def generate_comparison_table(
     target_payoff: Callable[[float], float],
@@ -153,27 +153,35 @@ def generate_comparison_table(
             approx_l1 += lambda_l1*S_test
             approx_weighted += lambda_weighted*S_test
         
-        # Calculate MAPE for each method
-        mape_l2 = calculate_mape(target_values, approx_l2)
-        mape_l1 = calculate_mape(target_values, approx_l1)
-        mape_weighted = calculate_mape(target_values, approx_weighted)
+        # Calculate MAE for each method
+        mae_l2 = calculate_mae(target_values, approx_l2)
+        mae_l1 = calculate_mae(target_values, approx_l1)
+        mae_weighted = calculate_mae(target_values, approx_weighted)
         
-        results.append((reg, mape_l2, mape_l1, mape_weighted))
+        results.append((reg, mae_l2, mae_l1, mae_weighted))
     
     # Generate LaTeX table
     method_comp_tex = os.path.join(LATEX_DIR, "method_comparison.tex")
     with open(method_comp_tex, "w") as f:
         f.write(r"""\begin{table}[htbp]
 \centering
-\caption{Performance Comparison of Different Regularization Methods}
+\caption{Performance Comparison of Different Regularization Methods (MAE)}
 \label{tab:method_comparison}
 \begin{tabular}{cccc}
 \hline
-$\gamma$ & L2 MAPE (\%) & L1 MAPE (\%) & Weighted MAPE (\%) \\
+$\gamma$ & L2 & L1 & Weighted \\
 \hline
 """)
-        for reg, mape_l2, mape_l1, mape_weighted in results:
-            f.write(f"{reg:.3f} & {mape_l2:.2f} & {mape_l1:.2f} & {mape_weighted:.2f} \\\\\n")
[…]

### 2025-02-19 latex/article.tex
strange format

--- 2025-02-19 latex/article.tex
@@
 
+\input{method_comparison.tex}
+
+The empirical results presented in Table~\ref{tab:method_comparison} demonstrate clear 
+superiority of the weighted error method across all regularization parameters. While the 
+L2 regularization provides an analytical solution, making it computationally attractive, 
+the weighted method consistently achieves MAE around 1.04, significantly outperforming 
+both L1 and L2 approaches. The L2 method shows stable but inferior performance with MAE 
+around 1.45, while L1 regularization's performance deteriorates significantly as $\gamma$ 
+increases, with MAE growing from 1.45 to 4.62.
+
+This comprehensive comparison suggests that for practical applications, the weighted error 
+method should be preferred despite its requirement for numerical optimization. The improved 
+accuracy (approximately 30\% reduction in MAE compared to L2) and consistent performance 
+across different regularization parameters justify the additional computational cost. 
+Furthermore, the weighted method's focus on economically significant regions makes it 
+particularly well-suited for real-world trading applications.
+
 \section{Results}
@@
         \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
-        \lambda \text{Var}\left(\hat{V}(S_T;\boldsymbol{\theta})\right)
 \end{equation}
-
-where $\lambda$ represents risk aversion parameter.
 

### 2025-02-19 latex/article.tex
without numerical implementation

@@
 the position weights, \( \gamma \) is the regularization parameter, and 
-\( S_{\min}, S_{\max} \) define the approximation domain. The L2 norm promotes 
-smoother weight distributions, providing stability to the solution.
+\( S_{\min}, S_{\max} \) define the approximation domain.
 
+\begin{figure}[htbp]
+\centering
+\input{regularization_comparison.tex}
+\caption{Comparison of L1 and L2 regularization}
+\label{fig:regularization}
+\end{figure}
+
+The L2 norm promotes smoother weight distributions, providing stability to the solution.
 Discretizing the integral and using matrix notation, we obtain:
@@
     \end{equation}
-    This formulation provides error weighting proportional to the target payoff magnitude, 
-    offering economic interpretation well-aligned with trading objectives. Furthermore, it 
-    naturally enhances focus on regions with significant payoff values, making it particularly 
-    suitable for practical applications.
 \end{enumerate}
-
-However, these generalizations lose the analytical tractability of the L2 case, 
-requiring numerical optimization methods for solution.
-
-\subsection{Numerical Implementation}
-The implementation leverages the analytical solution derived in the Mathematical Framework 
-section for L2-regularized problems. For L1 regularization and alternative loss functions, 
-numerical optimization methods are employed.
-
-\begin{figure}[htbp]
-\centering
-\input{regularization_comparison.tex}
-\caption{Comparison of L1 and L2 regularization}
-\label{fig:regularization}
-\end{figure}
-
-Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization 
-approaches in approximating a complex payoff profile. The target function combines 
-different types of functions, presenting a challenging test case. Both 
-methods achieve good approximation quality, with L2 regularization providing slightly 
-smoother results and L1 regularization favoring a sparser representation with fewer 
-non-zero option weights.
 
@@
 
-Figure~\ref{fig:weighted} illustrates the performance of the weighted error method, 
-which places greater emphasis on accurately approximating regions with larger payoff 
-values. This approach is particularly useful when the economic significance of errors 
-varies with the magnitude of the target payoff, providing a more practical solution 
-for trading applications.
+The weighted error formulation provides error weighting proportional to the target payoff magnitude, 
+offering economic interpretation well-aligned with trading objectives. Furthermore, it 
+naturally enhances focus on regions with significant payoff values, making it particularly 
+suitable for practical applications.
 
@@
 across different regularization parameters justify the additional computational cost.
-Furthermore, the weighted method's focus on economically significant regions makes it 
-particularly well-suited for real-world trading applications.
 
@@
     \argmax_{\boldsymbol{\theta}} 
-        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
+        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right]
 \end{equation}

### 2025-02-19 latex/article.tex
removed risk parameter in trading
comparison

--- 2025-02-19 latex/article.tex
@@
 \input{regularization_comparison.tex}
-\caption{Comparison of L1 and L2 regularization}
+\caption{Comparison of L1 and L2 regularization methods in approximating a complex payoff profile. 
+While both methods achieve reasonable approximation quality, L2 regularization provides smoother results 
+and L1 regularization favors a sparser representation with fewer non-zero option weights.}
 \label{fig:regularization}
 \end{figure}
-
-Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization 
-approaches in approximating a complex payoff profile. The target function combines 
-different types of functions, presenting a challenging test case. Both 
-methods achieve good approximation quality, with L2 regularization providing slightly 
-smoother results and L1 regularization favoring a sparser representation with fewer 
-non-zero option weights.
 
@@
 \input{weighted_loss.tex}
-\caption{Weighted Error Method Performance}
+\caption{Performance of the weighted error method, demonstrating superior accuracy in regions 
+with larger payoff values. This approach provides more economically meaningful results by 
+emphasizing the approximation quality where it matters most for trading applications.}
 \label{fig:weighted}
 \end{figure}
-
-Figure~\ref{fig:weighted} illustrates the performance of the weighted error method, 
-which places greater emphasis on accurately approximating regions with larger payoff 
-values. This approach is particularly useful when the economic significance of errors 
-varies with the magnitude of the target payoff, providing a more practical solution 
-for trading applications.
-
-\section{Results}
-\subsection{Distribution-Based Trading}
-The approximation method enables novel trading strategies that exploit distributional 
-forecasts rather than direct price predictions. Traders can hedge against forecasted 
-distribution features, express views on higher moments of price distribution, and 
-implement volatility surface arbitrage strategies through carefully constructed 
-option portfolios.
-
-The key advantage emerges when combining the approximation with distribution 
-forecasts $\mathbb{P}(S_T)$:
-
-\begin{equation}
-\mathbb{E}[V(S_T)] = 
-    \int_{0}^{\infty} 
-        V(S) \mathbb{P}(S_T = S) dS
-\end{equation}
-
-Optimal portfolio weights $\boldsymbol{\theta}^*$ maximize the expected payoff under 
-forecasted distribution:
-
-\begin{equation}
-\boldsymbol{\theta}^* = 
-    \argmax_{\boldsymbol{\theta}} 
-        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
-        \lambda \text{Var}\left(\hat{V}(S_T;\boldsymbol{\theta})\right)
-\end{equation}
-
-where $\lambda$ represents risk aversion parameter.
 
@@
 \begin{itemize}
-    \item L2 regularization provides consistent performance across different $\gamma$ values,
-    showing good stability in the approximation.
-    \item L1 regularization achieves comparable accuracy while promoting sparser solutions,
-    which can be advantageous for portfolio implementation.
-    \item The weighted error method shows improved accuracy in regions with larger payoff
-    values, as reflected in its MAE scores, particularly for moderate regularization values.
+    \item While L2 regularization provides an analytical solution and shows consistent performance 
+    (MAE ~1.45), it may not be the optimal choice for practical applications.
+    \item L1 regularization achieves comparable accuracy for low $\gamma$ values while promoting 
+    sparser solutions, but its performance deteriorates significantly as regularization increases.
+    \item The weighted error method consistently outperforms both L1 and L2 approaches, maintaining 
+    superior accuracy (MAE ~1.04) across all tested regularization values. This makes it the most 
+    suitable choice for real-world trading applications, where accuracy in high-payoff regions is 
+    crucial for portfolio performance.
 \end{itemize}
+
+Despite the mathematical elegance and analytical tractability of the L2 approach, the empirical 
+results strongly suggest that the weighted error method is more appropriate for practical 
+implementation. Its ability to focus on economically significant regions and maintain consistent 
+performance across different regularization parameters makes it the preferred choice for 
+real-world trading applications.
 

### 2025-02-19 latex/article.tex

@@
     \end{equation}
-    This formulation provides error weighting proportional to the target payoff magnitude, 
-    offering economic interpretation well-aligned with trading objectives. Furthermore, it 
-    naturally enhances focus on regions with significant payoff values, making it particularly 
-    suitable for practical applications.
 \end{enumerate}

### 2025-02-19 latex/article.tex
good looking
conclusion

--- 2025-02-19 latex/article.tex
@@
 
+\input{method_comparison.tex}
+
+Table~\ref{tab:method_comparison} presents a comparative analysis of the three regularization 
+methods across different regularization parameters ($\gamma$). The Mean Absolute Error (MAE) 
+is used as the primary metric for comparison, providing a direct measure of approximation accuracy 
+in absolute terms. Lower MAE values indicate better approximation quality.
+
 \begin{figure}[htbp]
@@
 
-\input{method_comparison.tex}
-
-Table~\ref{tab:method_comparison} presents a comparative analysis of the three regularization 
-methods across different regularization parameters ($\gamma$). The Mean Absolute Error (MAE) 
-is used as the primary metric for comparison, providing a direct measure of approximation accuracy 
-in absolute terms. Lower MAE values indicate better approximation quality.
-
+\vspace{1em}
 The results demonstrate that:
@@
 \section{Conclusion}
+This paper presents a comprehensive framework for approximating complex payoff profiles using vanilla European options in discrete strike spaces.
+The methodology addresses several practical challenges in financial engineering while maintaining mathematical rigor and computational efficiency.
+The developed framework operates in discrete strike spaces, directly reflecting real market conditions and constraints that practitioners face in implementation.
+
+A significant contribution of this work lies in the systematic comparison of different portfolio construction approaches.
+The analysis encompasses traditional L2 regularization, which provides analytical tractability, L1 regularization for sparse solutions, and a novel weighted error optimization method.
+Through extensive empirical testing, we demonstrate that the weighted error optimization consistently outperforms conventional regularization approaches in economically significant regions of the payoff profile.
+This superior performance stems from its ability to focus the portfolio construction where it matters most, resulting in more reliable trading strategies.
+
+The framework's implementation guidelines strike a careful balance between computational efficiency and approximation accuracy.
+This balance is achieved through thoughtful parameter selection and optimization techniques, making the methodology particularly suitable for real-world applications where both precision and computational speed are crucial considerations.
+
+The empirical results conclusively demonstrate that while regularization methods offer mathematical elegance and analytical solutions in some cases, the weighted error optimization approach provides markedly superior results for practical trading applications by focusing on economically meaningful regions of the payoff profile.
+
+Looking forward, this research opens several promising avenues for future investigation.
+Dynamic rebalancing strategies could enhance the framework's adaptability to changing market conditions.
+Integration with machine learning-based distribution forecasting might improve the accuracy of underlying assumptions.
+Furthermore, extension to multi-asset scenarios would broaden the methodology's applicability.
+The framework's inherent flexibility suggests potential applications beyond traditional option markets, including emerging derivative products and alternative asset classes, positioning it as a valuable tool for modern financial engineering.
 

### 2025-02-19 code/distrofit.py
removed unused

@@ -1,103 +1,0 @@
-import numpy as np
-from typing import Callable
-import plotly.graph_objects as go
-from plotly.subplots import make_subplots
-
-class DistributionToPayoff:
-    """
-    Converts probability distribution forecast to payoff function
-    
-    Args:
-        price_bins (list[float]): List of price bin edges
-        probabilities (list[float]): Probability for each bin
-        payoff_scale (float): Scaling factor for payoff amounts
-    """
-    
-    def __init__(
-        self,
-        price_bins: list[float],
-        probabilities: list[float],
-        payoff_scale: float = 100.0
-    ):
-        self.price_bins = price_bins
-        self.probabilities = probabilities
-        self.payoff_scale = payoff_scale
-        
-        if len(price_bins) != len(probabilities) + 1:
-            raise ValueError("Length of price_bins must be one more than probabilities")
-    
-    def get_payoff_function(self) -> Callable[[float], float]:
-        """Create piecewise constant payoff function"""
-        
-        # Ensure probabilities sum to 1
-        self.probabilities = np.array(self.probabilities) / sum(self.probabilities)
-        
-        # Calculate payoff weights: inverse probability weighting
-        weights = self.payoff_scale * (1 / (self.probabilities + 1e-8))
-        
-        # Create piecewise constant function
-        bins = self.price_bins
-        
-        def payoff(S: float) -> float:
-            for i, (lower, upper) in enumerate(zip(bins[:-1], bins[1:])):
-                if lower <= S < upper:
-                    return weights[i]
-            return 0.0
-        
-        return payoff
-    
-    def plot_distribution(self):
-        """Visualize probability distribution and payoff function in browser"""
-        
-        # Create figure with secondary y-axis
-        fig = make_subplots(rows=2, cols=1)
-        
-        # Plot probability distribution
-        bin_centers = [(a + b)/2 for a, b in zip(self.price_bins[:-1], self.price_bins[1:])]
-        fig.add_trace(
-            go.Bar(x=bin_centers, y=self.probabilities, name="Probability Distribution"),
-            row=1, col=1
-        )
-        
-        # Plot payoff function
-        S = np.linspace(min(self.price_bins), max(self.price_bins), 1000)
-        payoffs = [self.get_payoff_function()(x) for x in S]
-        fig.add_trace(
[…]

### 2025-02-19 code/distrofit_2.py

@@ -1,99 +1,0 @@
-import numpy as np
-from typing import Callable
-import matplotlib.pyplot as plt
-
-class DistributionToPayoff:
-    """
-    Converts probability distribution forecast to payoff function
-    
-    Args:
-        price_bins (list[float]): List of price bin edges
-        probabilities (list[float]): Probability for each bin
-        payoff_scale (float): Scaling factor for payoff amounts
-    """
-    
-    def __init__(
-        self,
-        price_bins: list[float],
-        probabilities: list[float],
-        payoff_scale: float = 100.0
-    ):
-        self.price_bins = price_bins
-        self.probabilities = probabilities
-        self.payoff_scale = payoff_scale
-        
-        if len(price_bins) != len(probabilities) + 1:
-            raise ValueError("Length of price_bins must be one more than probabilities")
-    
-    def get_payoff_function(self) -> Callable[[float], float]:
-        """Create piecewise constant payoff function"""
-        
-        # Ensure probabilities sum to 1
-        self.probabilities = np.array(self.probabilities) / sum(self.probabilities)
-        
-        # Calculate payoff weights: inverse probability weighting
-        weights = self.payoff_scale * (1 / (self.probabilities + 1e-8))
-        
-        # Create piecewise constant function
-        bins = self.price_bins
-        
-        def payoff(S: float) -> float:
-            for i, (lower, upper) in enumerate(zip(bins[:-1], bins[1:])):
-                if lower <= S < upper:
-                    return weights[i]
-            return 0.0
-        
-        return payoff
-    
-    def plot_distribution(self, save_path: str | None = None):
-        """Visualize probability distribution and payoff function"""
-        
-        fig, (ax1, ax2) = plt.subplots(2, 1, figsize=(10, 8))
-        
-        # Plot probability distribution
-        ax1.bar(
-            [(a + b)/2 for a, b in zip(self.price_bins[:-1], self.price_bins[1:])],
-            self.probabilities,
-            width=np.diff(self.price_bins),
-            alpha=0.5
-        )
-        ax1.set_title("Probability Distribution")
-        ax1.set_xlabel("Price")
-        ax1.set_ylabel("Probability")
-        
-        # Plot payoff function
-        S = np.linspace(min(self.price_bins), max(self.price_bins), 1000)
[…]

### 2025-02-19 code/pricing.py

@@ -1,75 +1,0 @@
-from math import log, sqrt, exp
-from scipy.stats import norm
-
-def black_scholes_price(
-    S: float,         # Current asset price
-    K: float,         # Strike price
-    T: float,         # Time to maturity (in years)
-    r: float,         # Risk-free interest rate
-    sigma: float,     # Asset volatility
-    option_type: str  # Option type: 'call' or 'put'
-) -> float:
-    """
-    Calculates the price of a European option using the Black-Scholes model.
-
-    Parameters:
-    S: Current asset price
-    K: Strike price
-    T: Time to maturity
-    r: Risk-free interest rate
-    sigma: Asset volatility
-    option_type: Option type ('call' or 'put')
-
-    Returns:
-    Option price
-    """
-    d1 = (log(S / K) + (r + 0.5 * sigma**2) * T) / (sigma * sqrt(T))
-    d2 = d1 - sigma * sqrt(T)
-    
-    if option_type == 'call':
-        price = S * norm.cdf(d1) - K * exp(-r * T) * norm.cdf(d2)
-    elif option_type == 'put':
-        price = K * exp(-r * T) * norm.cdf(-d2) - S * norm.cdf(-d1)
-    else:
-        raise ValueError("Unsupported option type. Use 'call' or 'put'.")
-    
-    return price
-
-
-def black_scholes_greeks(
-    S: float, K: float, T: float, r: float, sigma: float, option_type: str
-) -> dict[str, float]:
-    """
-    Calculates the Greeks for a European option using the Black-Scholes model.
-
-    Parameters:
-    S: Current asset price
-    K: Strike price
-    T: Time to maturity
-    r: Risk-free interest rate
-    sigma: Asset volatility
-    option_type: Option type ('call' or 'put')
-
-    Returns:
-    Dictionary with Greeks: delta, gamma, vega, theta, rho
-    """
-    d1 = (log(S / K) + (r + 0.5 * sigma**2) * T) / (sigma * sqrt(T))
-    d2 = d1 - sigma * sqrt(T)
-    
-    delta = norm.cdf(d1) if option_type == 'call' else -norm.cdf(-d1)
-    gamma = norm.pdf(d1) / (S * sigma * sqrt(T))
-    vega = S * norm.pdf(d1) * sqrt(T)
-    theta = (-S * norm.pdf(d1) * sigma / (2 * sqrt(T)) 
[…]

### 2025-02-19 latex/article.tex
link
proportional;

@@
 allows for the decomposition of arbitrary payoff structures into a series of call and
-put options with varying strike prices. The approach is validated through numerical
-examples and practical applications in financial engineering. The results demonstrate
-the effectiveness of this method in replicating complex payoffs.
+put options with varying strike prices. A key innovation is making the target payoff
+directly proportional to the estimated probability density function of the underlying
+asset price at expiration. The approach is validated through numerical examples and
+practical applications in financial engineering. The results demonstrate the effectiveness
+of this method in replicating complex payoffs while capturing the expected price
+distribution.
 \end{abstract}
@@
 options, due to their simplicity and widespread availability, serve as ideal 
-building blocks for such approximations. This paper introduces an approach to 
-approximating arbitrary payoff profiles using a combination of these options.
+building blocks for such approximations. This paper introduces an innovative approach 
+to approximating arbitrary payoff profiles using a combination of these options, where 
+the target payoff is designed to be directly proportional to the estimated probability 
+density function (PDF) of the underlying asset price at expiration.
 
@@
 The presented approach addresses these limitations by embracing the stochastic nature of markets
-without imposing restrictive distributional assumptions. Instead of attempting to fit
-market behavior into predetermined probability distributions as in \citep{Kuang2023} and 
-\citep{Li2023}, this paper proposes a framework that can accommodate any empirically 
-observed distribution. This distribution-free modeling approach acknowledges the complex, 
-non-Gaussian nature of market price movements, which often exhibit fat tails and 
-asymmetric behavior. It allows for direct incorporation of empirical distribution forecasts, 
-enabling more accurate risk assessment and pricing.
+and explicitly incorporating the estimated price distribution into the payoff structure. Instead 
+of attempting to fit market behavior into predetermined probability distributions as in 
+\citep{Kuang2023} and \citep{Li2023}, this paper proposes a framework that constructs payoff 
+profiles directly proportional to the empirically observed or forecasted price distribution. 
+This distribution-driven modeling approach acknowledges the complex, non-Gaussian nature of 
+market price movements, which often exhibit fat tails and asymmetric behavior. By making the 
+payoff proportional to the estimated PDF, the framework naturally adapts to the expected price 
+dynamics, providing enhanced risk-adjusted returns when the distribution forecast is accurate.
+
 Furthermore, the framework provides a flexible mechanism for extracting value from market
-inefficiencies without relying on specific distributional assumptions, while being able
-to adapt to changing market conditions and regime shifts that affect the shape of price
+inefficiencies by aligning portfolio returns with predicted price distributions, while being 
+able to adapt to changing market conditions and regime shifts that affect the shape of price
 distributions.
@@
 and observed market behavior by providing a practical framework for implementing
-distribution-based trading strategies. By focusing on distribution forecasting
-rather than point predictions, traders can develop more robust strategies that
-account for the full spectrum of possible market outcomes.
+distribution-based trading strategies. By focusing on distribution-proportional payoffs
+rather than arbitrary target functions, traders can develop more robust strategies that
+directly leverage their distributional views of market outcomes.
 
@@
 demonstrated the effectiveness of distribution-based predictions in capturing complex temporal 
-patterns. While tail risk hedging has been a fundamental concept since \citep{BlackScholes1973}, 
-where options were primarily used for downside protection, our approach extends this by 
-considering the entire distribution shape in portfolio construction. Unlike traditional methods 
-that focus solely on tail events, we propose a comprehensive framework that models and exploits 
-the complete probability distribution of asset returns.
+patterns. Our innovation lies in making the target payoff directly proportional to these 
+predicted distributions, creating a natural alignment between market views and portfolio returns. 
+While tail risk hedging has been a fundamental concept since \citep{BlackScholes1973}, where 
+options were primarily used for downside protection, our approach extends this by considering 
+the entire distribution shape in portfolio construction. Unlike traditional methods that focus 
+solely on tail events, we propose a comprehensive framework that models and exploits the 
+complete probability distribution of asset returns by making payoffs proportional to the 
+estimated PDF.
 
@@
     conditions.
+
+    \item \textbf{Distribution-Proportional Payoff:} The target payoff function is set to be
+    directly proportional to the estimated probability density function of the underlying
+    asset price at expiration, i.e., $V(S) \propto f(S)$ where $f(S)$ is the estimated PDF.
 \end{enumerate}
@@
 \subsection{Mathematical Framework}
-Let \( V(S) \) represent the value of a target payoff profile as a function of the 
-underlying asset price \( S \). We construct an approximation using \( n \) call 
-options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
+Let \( f(S) \) represent the estimated probability density function of the underlying asset
+price at expiration, and let \( V(S) = k f(S) \) be the target payoff profile, where \( k \)
+is a scaling constant. We construct an approximation using \( n \) call options and \( m \) 
+put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):
 
 \begin{equation}
-V(S) \approx \lambda S + 
+k f(S) \approx \lambda S + 
     \sum_{i=1}^{n} \alpha_i C(S, K_i) + 
@@
     \int_{S_{\min}}^{S_{\max}} 
-        \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
+        \left[ k f(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
     \gamma \|\boldsymbol{\theta}\|_2^2
@@
 evaluated at discrete price points \( \{S_k\}_{k=1}^N \), and \( \mathbf{b} \) is
-the vector of target payoff values.
+the vector of target payoff values proportional to the estimated PDF.
 
@@
             \int_{S_{\min}}^{S_{\max}} 
-                \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
+                \left[ k f(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
             \gamma \|\boldsymbol{\theta}\|_1
@@
             \int_{S_{\min}}^{S_{\max}} 
-                V(S) \Big| V(S) - \hat{V}(S;\boldsymbol{\theta}) \Big| dS + 
+                k f(S) \Big| k f(S) - \hat{V}(S;\boldsymbol{\theta}) \Big| dS + 
             \gamma \|\boldsymbol{\theta}\|_p^p
@@
     offering economic interpretation well-aligned with trading objectives. Furthermore, it 
-    naturally enhances focus on regions with significant payoff values, making it particularly 
+    naturally enhances focus on regions with significant probability mass, making it particularly 
     suitable for practical applications.
@@
 \input{regularization_comparison.tex}
-\caption{Comparison of L1 and L2 regularization methods in approximating a complex payoff profile. 
-While both methods achieve reasonable approximation quality, L2 regularization provides smoother results 
-and L1 regularization favors a sparser representation with fewer non-zero option weights.}
+\caption{Comparison of L1 and L2 regularization methods in approximating a PDF-proportional 
+payoff profile. While both methods achieve reasonable approximation quality, L2 regularization 
+provides smoother results and L1 regularization favors a sparser representation with fewer 
+non-zero option weights.}
 \label{fig:regularization}
@@
 \caption{Performance of the weighted error method, demonstrating superior accuracy in regions 
-with larger payoff values. This approach provides more economically meaningful results by 
-emphasizing the approximation quality where it matters most for trading applications.}
+with larger probability mass. This approach provides more economically meaningful results by 
+emphasizing the approximation quality where the underlying asset price is most likely to be 
+at expiration.}
 \label{fig:weighted}
@@
     superior accuracy (MAE ~1.04) across all tested regularization values. This makes it the most 
-    suitable choice for real-world trading applications, where accuracy in high-payoff regions is 
-    crucial for portfolio performance.
+    suitable choice for real-world trading applications, where accuracy in high-probability regions 
+    is crucial for portfolio performance.
 \end{itemize}
@@
 results strongly suggest that the weighted error method is more appropriate for practical 
-implementation. Its ability to focus on economically significant regions and maintain consistent 
-performance across different regularization parameters makes it the preferred choice for 
+implementation. Its ability to focus on regions with significant probability mass and maintain 
+consistent performance across different regularization parameters makes it the preferred choice for 
 real-world trading applications.
@@
 \section{Conclusion}
-This paper presents a comprehensive framework for approximating complex payoff profiles using vanilla European options in discrete strike spaces.
-The methodology addresses several practical challenges in financial engineering while maintaining mathematical rigor and computational efficiency.
-The developed framework operates in discrete strike spaces, directly reflecting real market conditions and constraints that practitioners face in implementation.
+This paper presents a comprehensive framework for approximating PDF-proportional payoff profiles 
+using vanilla European options in discrete strike spaces. The methodology addresses several 
+practical challenges in financial engineering while maintaining mathematical rigor and 
+computational efficiency. The developed framework operates in discrete strike spaces, directly 
+reflecting real market conditions and constraints that practitioners face in implementation.
 
-A significant contribution of this work lies in the systematic comparison of different portfolio construction approaches.
-The analysis encompasses traditional L2 regularization, which provides analytical tractability, L1 regularization for sparse solutions, and a novel weighted error optimization method.
-Through extensive empirical testing, we demonstrate that the weighted error optimization consistently outperforms conventional regularization approaches in economically significant regions of the payoff profile.
-This superior performance stems from its ability to focus the portfolio construction where it matters most, resulting in more reliable trading strategies.
+A significant contribution of this work lies in the systematic comparison of different portfolio 
+construction approaches and the novel idea of making payoffs directly proportional to estimated 
+price distributions. The analysis encompasses traditional L2 regularization, which provides 
+analytical tractability, L1 regularization for sparse solutions, and a novel weighted error 
+optimization method. Through extensive empirical testing, we demonstrate that the weighted error 
+optimization consistently outperforms conventional regularization approaches in regions with 
+significant probability mass. This superior performance stems from its ability to focus the 
+portfolio construction where the underlying asset price is most likely to be at expiration, 
+resulting in more reliable trading strategies.
 
-The framework's implementation guidelines strike a careful balance between computational efficiency and approximation accuracy.
-This balance is achieved through thoughtful parameter selection and optimization techniques, making the methodology particularly suitable for real-world applications where both precision and computational speed are crucial considerations.
+The framework's implementation guidelines strike a careful balance between computational efficiency 
+and approximation accuracy. This balance is achieved through thoughtful parameter selection and 
+optimization techniques, making the methodology particularly suitable for real-world applications 
+where both precision and computational speed are crucial considerations.
 
-The empirical results conclusively demonstrate that while regularization methods offer mathematical elegance and analytical solutions in some cases, the weighted error optimization approach provides markedly superior results for practical trading applications by focusing on economically meaningful regions of the payoff profile.
+The empirical results conclusively demonstrate that while regularization methods offer mathematical 
+elegance and analytical solutions in some cases, the weighted error optimization approach provides 
+markedly superior results for practical trading applications by focusing on regions with significant 
+probability mass in the estimated price distribution.
 
-Looking forward, this research opens several promising avenues for future investigation.
-Dynamic rebalancing strategies could enhance the framework's adaptability to changing market conditions.
-Integration with machine learning-based distribution forecasting might improve the accuracy of underlying assumptions.
-Furthermore, extension to multi-asset scenarios would broaden the methodology's applicability.
-The framework's inherent flexibility suggests potential applications beyond traditional option markets, including emerging derivative products and alternative asset classes, positioning it as a valuable tool for modern financial engineering.
+Looking forward, this research opens several promising avenues for future investigation. Dynamic 
+rebalancing strategies could enhance the framework's adaptability to changing market conditions. 
+Integration with machine learning-based distribution forecasting might improve the accuracy of 
+underlying assumptions. Furthermore, extension to multi-asset scenarios would broaden the 
+methodology's applicability. The framework's inherent flexibility suggests potential applications 
+beyond traditional option markets, including emerging derivative products and alternative asset 
+classes, positioning it as a valuable tool for modern financial engineering.
+
+The source code of the numerical experiments is available on \href{https://github.com/VladKochetov007/payoff_approximation}{GitHub}.
 

### 2025-02-23 code/approximation.py
0 reg

@@ -327,7 +327,7 @@ def example_usage():
         print(f"Spot position: {lambda_weighted:.2f}")
         
     # Generate comparison table for different regularization values
-    regularization_values = [0.01, 0.05, 0.1, 0.5, 10]
+    regularization_values = [0, 0.01, 0.05, 0.1, 0.5, 10]
     generate_comparison_table(target, strikes, spot=100, regularization_values=regularization_values)
 
 if __name__ == "__main__":
